### 2015-09-07 paper.tex
first commit of draft

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\begin{document}
\title{Upgrades to the SINQ Cold Neutron Source}

\author{R. M.Bergmann, U. Filges, D. Kiselev, T. Reiss, V. Talanov, M. Wohlmuther}

\address{Paul Scherrer Institut, 5232 Villigen, Switzerland}

\ead{ryan.bergmann@psi.ch}

\begin{abstract}Changing the configuration of the cold neutron source during an extended shutdown of Swiss Spallation Neutron Source (SINQ) is being considered for improving performance of the instruments that use the cold source.  The cold neutron source consists of a 20 L volume of liquid D2 at approximately 25 K.  Previous upgrades included adding a re-entrant hole into one side of the D2 volume to allow cold neutrons to stream uninhibited from the center of the source towards the instrument neutron guides.  Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.6, with gains increasing with wavelength. These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided.  Voiding the re-entrant hole relies on radiative heating to boil D2 which in turn fills the re-entrant hole cavity, pushing the liquid D2 out.  Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D2), removing some extra structural material around the D2 tank, redesigning the re-entrant hole geometry to be more optically ideal, introducing a Pb-208 reflector to minimize cold neutron up-scattering from the surrounding D2O moderator tank, and implementing a small liquid H2 volume to provide a cold neutron “hot spot” for certain instruments.  These changes are predicted to increase neutron fluence between 1.1 to 2.0 times the current levels, depending on instrument location, view, and wavelengths of interest.
\end{abstract}

\section{Introduction}
These guidelines show how to prepare articles for publication in \jpcs\ using \LaTeX\ so they can be published quickly and accurately. Articles will be refereed by the \corg s but the accepted PDF will be published with no editing, proofreading or changes to layout. It is, therefore, the author's responsibility to ensure that the content and layout are correct.  This document has been prepared using \cls\ so serves as a sample document. The class file and accompanying documentation are available from \verb"http://jpcs.iop.org".

\section{Preparing your paper}
\verb"jpconf" requires \LaTeXe\ and  can be used with other package files such
as those loading the AMS extension fonts 
\verb"msam" and \verb"msbm" (these fonts provide the 
blackboard bold alphabet and various extra maths symbols as well as 
symbols useful in figure captions); an extra style file \verb"iopams.sty" is 
provided to load these packages and provide extra definitions for bold Greek letters. 
\subsection{Headers, footers and page numbers}
Authors should {\it not} add headers, footers or page numbers to the pages of their article---they will
be added by \iopp\ as part of the production process.

\subsection{{\cls\ }package options}
The \cls\ class file has two options `a4paper' and `letterpaper':
\begin{verbatim}
\documentclass[a4paper]{jpconf}
\end{verbatim}

or \begin{verbatim}
\documentclass[letterpaper]{jpconf}
\end{verbatim}

\begin{center}
\begin{table}[h]
\caption{\label{opt}\cls\ class file options.}
%\footnotesize\rm
\centering
\begin{tabular}{@{}*{7}{l}}
\br
Option&Description\\
\mr
\verb"a4paper"&Set the paper size and margins for A4 paper.\\
\verb"letterpaper"&Set the paper size and margins for US letter paper.\\
\br
\end{tabular}
\end{table}
\end{center}

The default paper size is A4 (i.e., the default option is {\tt a4paper}) but this can be changed to Letter by 
using \verb"\documentclass[letterpaper]{jpconf}". It is essential that you do not put macros into the text which alter the page dimensions.

\section{The title, authors, addresses and abstract} 
The code for setting the title page information is slightly different from
the normal default in \LaTeX\ but please follow these instructions as carefully as possible so all articles within a conference have the same style to the title page. 
The title is set in bold unjustified type using the command
\verb"\title{#1}", where \verb"#1" is the title of the article. The
first letter of the title should be capitalized with the rest in lower case. 
The next information required is the list of all authors' names followed by 
the affiliations. For the authors' names type \verb"\author{#1}", 
where \verb"#1" is the 
list of all authors' names. The style for the names is initials then
surname, with a comma after all but the last 
two names, which are separated by `and'. Initials should {\it not} have 
full stops. First names may be used if desired. The command \verb"\maketitle" is not
required.

The addresses of the authors' affiliations follow the list of authors. 
Each address should be set by using
\verb"\address{#1}" with the address as the single parameter in braces. 
If there is more 
than one address then a superscripted number, followed by a space, should come at the start of
each address. In this case each author should also have a superscripted number or numbers following their name to indicate which address is the appropriate one for them.

Please also provide e-mail addresses for any or all of the authors using an \verb"\ead{#1}" command after the last address. \verb"\ead{#1}" provides the text Email: so \verb"#1" is just the e-mail address or a list of emails.

The abstract follows the addresses and
should give readers concise information about the content 
of the article and should not normally exceed 200 
words. {\bf All articles must include an abstract}. To indicate the start 
of the abstract type \verb"\begin{abstract}" followed by the text of the 
abstract.  The abstract should normally be restricted 
to a single paragraph and is terminated by the command
\verb"\end{abstract}"

\subsection{Sample coding for the start of an article}
\label{startsample}
The code for the start of a title page of a typical paper might read:
\begin{verbatim}
\title{The anomalous magnetic moment of the 
neutrino and its relation to the solar neutrino problem}

\author{P J Smith$^1$, T M Collins$^2$, 
R J Jones$^{3,}$\footnote[4]{Present address:
Department of Physics, University of Bristol, Tyndalls Park Road, 
Bristol BS8 1TS, UK.} and Janet Williams$^3$}

\address{$^1$ Mathematics Faculty, Open University, 
Milton Keynes MK7~6AA, UK}
\address{$^2$ Department of Mathematics, 
Imperial College, Prince Consort Road, London SW7~2BZ, UK}
\address{$^3$ Department of Computer Science, 
University College London, Gower Street, London WC1E~6BT, UK}

\ead{williams@ucl.ac.uk}

\begin{abstract}
The abstract appears here.
\end{abstract}
\end{verbatim}

\section{The text}
The text of the article should should be produced using standard \LaTeX\ formatting. Articles may be divided into sections and subsections, but the length limit provided by the \corg\ should be adhered to.

\subsection{Acknowledgments}
Authors wishing to acknowledge assistance or encouragement from 
colleagues, special work by technical staff or financial support from 
organizations should do so in an unnumbered Acknowledgments section 
immediately following the last numbered section of the paper. The 
command \verb"\ack" sets the acknowledgments heading as an unnumbered
section.

\subsection{Appendices}
Technical detail that it is necessary to include, but that interrupts 
the flow of the article, may be consigned to an appendix. 
Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
If there are two or more appendices they will be called Appendix A, Appendix B, etc. 
Numbered equations will be in the form (A.1), (A.2), etc,
figures will appear as figure A1, figure B1, etc and tables as table A1,
table B1, etc.

The command \verb"\appendix" is used to signify the start of the
appendixes. Thereafter \verb"\section", \verb"\subsection", etc, will 
give headings appropriate for an appendix. To obtain a simple heading of 
`Appendix' use the code \verb"\section*{Appendix}". If it contains
numbered equations, figures or tables the command \verb"\appendix" should
precede it and \verb"\setcounter{section}{1}" must follow it.

\section{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the online version of \jpcs\ references will be linked to their original source or to the article within a secondary service such as INSPEC or ChemPort wherever possible. To facilitate this linking extra care should be taken when preparing reference lists.

Two different styles of referencing are in common use: the Harvard alphabetical system and the Vancouver numerical system.  For \jpcs, the Vancouver numerical system is preferred but authors should use the Harvard alphabetical system if they wish to do so. In the numerical system references are numbered sequentially throughout the text within square brackets, like this [2], and one number can be used to designate several references.

\subsection{Using \BibTeX}
We highly recommend the {\ttfamily\textbf\selectfont iopart-num} \BibTeX\ package by Mark~A~Caprio \cite{iopartnum}, which is included with this documentation.

\subsection{Reference lists}
A complete reference should provide the reader with enough information to locate the article concerned, whether published in print or electronic form, and should, depending on the type of reference, consist of:

\begin{itemize}
\item name(s) and initials;
\item date published;
\item title of journal, book or other publication; 
\item titles of journal articles may also be included (optional);
\item volume number;
\item editors, if any;
\item town of publication and publisher in parentheses for {\it books};
\item the page numbers.
\end{itemize}

Up to ten authors may be given in a particular reference; where 
there are more than ten only the first should be given followed by 
`{\it et al}'. If an author is unsure of a particular journal's abbreviated title it is best to leave the title in 
full. The terms {\it loc.\ cit.\ }and {\it ibid.\ }should not be used. 
Unpublished conferences and reports should generally not be included 
in the reference list and articles in the course of publication should 
be entered only if the journal of publication is known. 
A thesis submitted for a higher degree may be included 
in the reference list if it has not been superseded by a published 
paper and is available through a library; sufficient information 
should be given for it to be traced readily.

\subsection{Formatting reference lists}
Numeric reference lists should contain the references within an unnumbered section (such as \verb"\section*{References}"). The 
reference list itself is started by the code 
\verb"\begin{thebibliography}{<num>}", where \verb"<num>" is the largest
number in the reference list and is completed by
\verb"\end{thebibliography}". 
Each reference starts with \verb"\bibitem{<label>}", where `label' is the label used for cross-referencing. Each \verb"\bibitem" should only contain a reference to a single article (or a single article and a preprint reference to the same article).  When one number actually covers a group of two or more references to different articles, \verb"\nonum"
should replace \verb"\bibitem{<label>}" at
the start of each reference in the group after the first.

For an alphabetic reference list use \verb"\begin{thereferences}" ... \verb"\end{thereferences}" instead of the
`thebibliography' environment and each reference can be start with just \verb"\item" instead of \verb"\bibitem{label}"
as cross referencing is less useful for alphabetic references.

\subsection {References to printed journal articles}
A normal reference to a journal article contains three changes of font (see table \ref{jfonts}) and is constructed as follows:

\begin{itemize}
\item the authors should be in the form surname (with only the first letter capitalized) followed by the initials with no periods after the initials. Authors should be separated by a comma except for the last two which should be separated by `and' with no comma preceding it;
\item the article title (if given) should be in lower case letters, except for an initial capital, and should follow the date;
\item the journal title is in italic and is abbreviated. If a journal has several parts denoted by different letters the part letter should be inserted after the journal in Roman type, e.g. {\it Phys. Rev.} A;
\item the volume number should be in bold type;
\item both the initial and final page numbers should be given where possible. The final page number should be in the shortest possible form and separated from the initial page number by an en rule `-- ', e.g. 1203--14, i.e. the numbers `12' are not repeated.
\end{itemize}

A typical (numerical) reference list might begin

\medskip
\begin{thebibliography}{9}
\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
{\it J. Appl. Phys}. {\bf 87} 965 
\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
{\it Electron. Lett.} {\bf 32} 1105 
\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
{\it J. Appl. Phys.} {\bf 83} 826 
\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
\end{thebibliography}
\smallskip

\noindent which would be obtained by typing

\begin{verbatim}
\begin{\thebibliography}{9}
\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
{\it J. Appl. Phys}. {\bf 87} 965 
\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
{\it Electron. Lett.} {\bf 32} 1105 
\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
{\it J. Appl. Phys.} {\bf 83} 826 
\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
\end{\thebibliography}
\end{verbatim}

\begin{center}
\begin{table}[h]
\centering
\caption{\label{jfonts}Font styles for a reference to a journal article.} 
\begin{tabular}{@{}l*{15}{l}}
\br
Element&Style\\
\mr
Authors&Roman type\\
Date&Roman type\\
Article title (optional)&Roman type\\
Journal title&Italic type\\
Volume number&Bold type\\
Page numbers&Roman type\\
\br
\end{tabular}
\end{table}
\end{center}

\subsection{References to \jpcs\ articles}
Each conference proceeding published in \jpcs\ will be a separate {\it volume}; 
references should follow the style for conventional printed journals. For example:\vspace{6pt}
\numrefs{1}
\item Douglas G 2004 \textit{J. Phys.: Conf. Series} \textbf{1} 23--36
\endnumrefs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{References to preprints}
For preprints there are two distinct cases:
\renewcommand{\theenumi}{\arabic{enumi}}
\begin{enumerate}
\item Where the article has been published in a journal and the preprint is supplementary reference information. In this case it should be presented as:
\medskip
\numrefs{1}
\item Kunze K 2003 T-duality and Penrose limits of spatially homogeneous and inhomogeneous cosmologies {\it Phys. Rev.} D {\bf 68} 063517 ({\it Preprint} gr-qc/0303038)
\endnumrefs
\item Where the only reference available is the preprint. In this case it should be presented as
\medskip
\numrefs{1}
\item Milson R, Coley A, Pravda V and Pravdova A 2004 Alignment and algebraically special tensors {\it Preprint} gr-qc/0401010
\endnumrefs
\end{enumerate}

\subsection{References to electronic-only journals}
In general article numbers are given, and no page ranges, as most electronic-only journals start each article on page 1.

\begin{itemize} 
\item For {\it New Journal of Physics} (article number may have from one to three digits)
\numrefs{1}
\item Fischer R 2004 Bayesian group analysis of plasma-enhanced chemical vapour deposition data {\it New. J. Phys.} {\bf 6} 25 
\endnumrefs
\item For SISSA journals the volume is divided into monthly issues and these form part of the article number

\numrefs{2}
\item Horowitz G T and Maldacena J 2004 The black hole final state {\it J. High Energy Phys.}  	JHEP02(2004)008
\item Bentivegna E, Bonanno A and Reuter M 2004 Confronting the IR fixed point cosmology 	with 	high-redshift observations {\it J. Cosmol. Astropart. Phys.} JCAP01(2004)001  
\endnumrefs
\end{itemize}

\subsection{References to books, conference proceedings and reports}
References to books, proceedings and reports are similar to journal references, but have 
only two changes of font (see table~\ref{book}).

\begin{table}
\centering
\caption{\label{book}Font styles for references to books, conference proceedings and reports.}
\begin{tabular}{@{}l*{15}{l}}
\br
Element&Style\\
\mr
Authors&Roman type\\
Date&Roman type\\
Book title (optional)&Italic type\\
Editors&Roman type\\
Place (city, town etc) of publication&Roman type\\
Publisher&Roman type\\
Volume&Roman type\\
Page numbers&Roman type\\
\br
\end{tabular}
\end{table}

Points to note are:
\medskip
\begin{itemize}
\item Book titles are in italic and should be spelt out in full with initial capital letters for all except minor words. Words such as Proceedings, Symposium, International, Conference, Second, etc should be abbreviated to {\it Proc.}, {\it Symp.}, {\it Int.}, {\it Conf.}, {\it 2nd}, respectively, but the rest of the title should be given in full, followed by the date of the conference and the town or city where the conference was held. For Laboratory Reports the Laboratory should be spelt out wherever possible, e.g. {\it Argonne National Laboratory Report}.
\item The volume number, for example vol 2, should be followed by the editors, if any, in a form such as `ed A J Smith and P R Jones'. Use {\it et al} if there are more than two editors. Next comes the town of publication and publisher, within brackets and separated by a colon, and finally the page numbers preceded by p if only one number is given or pp if both the initial and final numbers are given.
\end{itemize}

Examples taken from published papers:
\medskip

\numrefs{99}
\item Kurata M 1982 {\it Numerical Analysis for Semiconductor Devices} (Lexington, MA: Heath)
\item Selberherr S 1984 {\it Analysis and Simulation of Semiconductor Devices} (Berlin: Springer)
\item Sze S M 1969 {\it Physics of Semiconductor Devices} (New York: Wiley-Interscience)
\item Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} (Moscow: Moscow State University Press) p 103
\item Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear Physics (Munich)} vol 1 (Amsterdam: 	North-Holland/American Elsevier) p 517
\item Cheng G X 2001 {\it Raman and Brillouin Scattering-Principles and Applications} (Beijing: Scientific) 
\item Szytula A and Leciejewicz J 1989 {\it Handbook on the Physics and Chemistry of Rare Earths} vol 12, ed K A Gschneidner Jr and L Erwin (Amsterdam: Elsevier) p 133
\item Kuhn T 1998 {\it Density matrix theory of coherent ultrafast dynamics Theory of Transport Properties of Semiconductor Nanostructures} (Electronic Materials vol 4) ed E Sch\"oll (London: Chapman and Hall) chapter 6 pp 173--214
\endnumrefs

\section{Tables and table captions}
Tables should be numbered serially and referred to in the text 
by number (table 1, etc, {\bf rather than} tab. 1). Each table should be a float and be positioned within the text at the most convenient place near to where it is first mentioned in the text. It should have an 
explanatory caption which should be as concise as possible.

\subsection{The basic table format}
The standard form for a table is:
\begin{verbatim}
\begin{table}
\caption{\label{label}Table caption.}
\begin{center}
\begin{tabular}{llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{center}
\end{table}
\end{verbatim}

The above code produces table~\ref{ex}.

\begin{table}[h]
\caption{\label{ex}Table caption.}
\begin{center}
\begin{tabular}{llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{center}
\end{table}

Points to note are:
\medskip
\begin{enumerate}
\item The caption comes before the table.
\item The normal style is for tables to be centred in the same way as
equations. This is accomplished
by using \verb"\begin{center}" \dots\ \verb"\end{center}".

\item The default alignment of columns should be aligned left.

\item Tables should have only horizontal rules and no vertical ones. The rules at
the top and bottom are thicker than internal rules and are set with
\verb"\br" (bold rule). 
The rule separating the headings from the entries is set with
\verb"\mr" (medium rule). These commands do not need a following double backslash.

\item Numbers in columns should be aligned as appropriate, usually on the decimal point;
to help do this a control sequence \verb"\lineup" has been defined 
which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
to be a space the width of a minus sign, and \verb"\-" to be a left
overlapping minus sign. \verb"\-" is for use in text mode while the other
two commands may be used in maths or text.
(\verb"\lineup" should only be used within a table
environment after the caption so that \verb"\-" has its normal meaning
elsewhere.) See table~\ref{tabone} for an example of a table where
\verb"\lineup" has been used.
\end{enumerate}

\begin{table}[h]
\caption{\label{tabone}A simple example produced using the standard table commands 
and $\backslash${\tt lineup} to assist in aligning columns on the 
decimal point. The width of the 
table and rules is set automatically by the 
preamble.}

\begin{center}
\lineup
\begin{tabular}{*{7}{l}}
\br                              
$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
\mr
\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
\br
\end{tabular}
\end{center}
\end{table}

\section{Figures and figure captions}
Figures must be included in the source code of an article at the appropriate place in the text not grouped together at the end.

Each figure should have a brief caption describing it and, if 
necessary, interpreting the various lines and symbols on the figure. 
As much lettering as possible should be removed from the figure itself and 
included in the caption. If a figure has parts, these should be 
labelled ($a$), ($b$), ($c$), etc. 
\Tref{blobs} gives the definitions for describing symbols and lines often
used within figure captions (more symbols are available
when using the optional packages loading the AMS extension fonts).

\begin{table}[h]
\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
captions.}
\begin{center}
\begin{tabular}{lllll}
\br
Control sequence&Output&&Control sequence&Output\\
\mr
\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
\br
\end{tabular}
\end{center}
\end{table}

Authors should try and use the space allocated to them as economically as possible. At times it may be convenient to put two figures side by side or the caption at the side of a figure. To put figures side by side, within a figure environment, put each figure and its caption into a minipage with an appropriate width (e.g. 3in or 18pc if the figures are of equal size) and then separate the figures slightly by adding some horizontal space between the two minipages (e.g. \verb"\hspace{.2in}" or \verb"\hspace{1.5pc}". To get the caption at the side of the figure add the small horizontal space after the \verb"\includegraphics" command and then put the \verb"\caption" within a minipage of the appropriate width aligned bottom, i.e. \verb"\begin{minipage}[b]{3in}" etc (see code in this file used to generate figures 1--3).

Note that it may be necessary to adjust the size of the figures (using optional arguments to \verb"\includegraphics", for instance \verb"[width=3in]") to get you article to fit within your page allowance or to obtain good page breaks.

\begin{figure}[h]
\begin{minipage}{14pc}
\includegraphics[width=14pc]{name.eps}
\caption{\label{label}Figure caption for first of two sided figures.}
\end{minipage}\hspace{2pc}%
\begin{minipage}{14pc}
\includegraphics[width=14pc]{name.eps}
\caption{\label{label}Figure caption for second of two sided figures.}
\end{minipage} 
\end{figure}

\begin{figure}[h]
\includegraphics[width=14pc]{name.eps}\hspace{2pc}%
\begin{minipage}[b]{14pc}\caption{\label{label}Figure caption for a narrow figure where the caption is put at the side of the figure.}
\end{minipage}
\end{figure}

Using the graphicx package figures can be included using code such as:
\begin{verbatim}
\begin{figure}
\begin{center}
\includegraphics{file.eps}
\end{center}
\caption{\label{label}Figure caption}
\end{figure}
\end{verbatim}

\section*{References}
\begin{thebibliography}{9}
\bibitem{iopartnum} IOP Publishing is to grateful Mark A Caprio, Center for Theoretical Physics, Yale University, for permission to include the {\tt iopart-num} \BibTeX package (version 2.0, December 21, 2006) with  this documentation. Updates and new releases of {\tt iopart-num} can be found on \verb"www.ctan.org" (CTAN). 
\end{thebibliography}

\end{document}

### 2015-09-07 paper.tex
removed instructions, added SNF acknowledgement

@@
 
-\author{R. M.Bergmann, U. Filges, D. Kiselev, T. Reiss, V. Talanov, M. Wohlmuther}
+\author{R M Bergmann, U Filges, D Kiselev, T Reiss, V Talanov and M Wohlmuther}
 
@@
 
+\ack{This work was supported by Swiss National Science Foundation grant 200021\_150048/1.}
+
 \section{Introduction}
-These guidelines show how to prepare articles for publication in \jpcs\ using \LaTeX\ so they can be published quickly and accurately.
-Articles will be refereed by the \corg s but the accepted PDF will be published with no editing, proofreading or changes to layout.
-It is, therefore, the author's responsibility to ensure that the content and layout are correct.
-This document has been prepared using \cls\ so serves as a sample document.
-The class file and accompanying documentation are available from \verb"http://jpcs.iop.org".
 
 \section{Preparing your paper}
-\verb"jpconf" requires \LaTeXe\ and  can be used with other package files such
-as those loading the AMS extension fonts 
-\verb"msam" and \verb"msbm" (these fonts provide the 
-blackboard bold alphabet and various extra maths symbols as well as 
-symbols useful in figure captions); an extra style file \verb"iopams.sty" is 
-provided to load these packages and provide extra definitions for bold Greek letters. 
-\subsection{Headers, footers and page numbers}
-Authors should {\it not} add headers, footers or page numbers to the pages of their article---they will
-be added by \iopp\ as part of the production process.
-
-\subsection{{\cls\ }package options}
-The \cls\ class file has two options `a4paper' and `letterpaper':
-\begin{verbatim}
-\documentclass[a4paper]{jpconf}
-\end{verbatim}
-
-or \begin{verbatim}
-\documentclass[letterpaper]{jpconf}
-\end{verbatim}
-
-\begin{center}
-\begin{table}[h]
-\caption{\label{opt}\cls\ class file options.}
-%\footnotesize\rm
-\centering
-\begin{tabular}{@{}*{7}{l}}
-\br
-Option&Description\\
-\mr
-\verb"a4paper"&Set the paper size and margins for A4 paper.\\
-\verb"letterpaper"&Set the paper size and margins for US letter paper.\\
-\br
-\end{tabular}
-\end{table}
-\end{center}
-
-The default paper size is A4 (i.e., the default option is {\tt a4paper}) but this can be changed to Letter by 
-using \verb"\documentclass[letterpaper]{jpconf}". It is essential that you do not put macros into the text which alter the page dimensions.
 
 \section{The title, authors, addresses and abstract}
-The code for setting the title page information is slightly different from
-the normal default in \LaTeX\ but please follow these instructions as carefully as possible so all articles within a conference have the same style to the title page. 
-The title is set in bold unjustified type using the command
-\verb"\title{#1}", where \verb"#1" is the title of the article. The
-first letter of the title should be capitalized with the rest in lower case. 
-The next information required is the list of all authors' names followed by 
-the affiliations. For the authors' names type \verb"\author{#1}", 
-where \verb"#1" is the 
-list of all authors' names. The style for the names is initials then
-surname, with a comma after all but the last 
-two names, which are separated by `and'. Initials should {\it not} have 
-full stops. First names may be used if desired. The command \verb"\maketitle" is not
-required.
-
-The addresses of the authors' affiliations follow the list of authors. 
-Each address should be set by using
-\verb"\address{#1}" with the address as the single parameter in braces. 
-If there is more 
-than one address then a superscripted number, followed by a space, should come at the start of
-each address. In this case each author should also have a superscripted number or numbers following their name to indicate which address is the appropriate one for them.
-
-Please also provide e-mail addresses for any or all of the authors using an \verb"\ead{#1}" command after the last address.
-\verb"\ead{#1}" provides the text Email: so \verb"#1" is just the e-mail address or a list of emails.
-
-The abstract follows the addresses and
-should give readers concise information about the content 
-of the article and should not normally exceed 200 
-words. {\bf All articles must include an abstract}. To indicate the start 
-of the abstract type \verb"\begin{abstract}" followed by the text of the 
-abstract.  The abstract should normally be restricted 
-to a single paragraph and is terminated by the command
-\verb"\end{abstract}"
 
 \subsection{Sample coding for the start of an article}
-\label{startsample}
-The code for the start of a title page of a typical paper might read:
-\begin{verbatim}
-\title{The anomalous magnetic moment of the 
-neutrino and its relation to the solar neutrino problem}
-
-\author{P J Smith$^1$, T M Collins$^2$, 
-R J Jones$^{3,}$\footnote[4]{Present address:
-Department of Physics, University of Bristol, Tyndalls Park Road, 
-Bristol BS8 1TS, UK.} and Janet Williams$^3$}
-
-\address{$^1$ Mathematics Faculty, Open University, 
-Milton Keynes MK7~6AA, UK}
-\address{$^2$ Department of Mathematics, 
-Imperial College, Prince Consort Road, London SW7~2BZ, UK}
-\address{$^3$ Department of Computer Science, 
-University College London, Gower Street, London WC1E~6BT, UK}
-
-\ead{williams@ucl.ac.uk}
-
-\begin{abstract}
-The abstract appears here.
-\end{abstract}
-\end{verbatim}
 
 \section{The text}
-The text of the article should should be produced using standard \LaTeX\ formatting.
-Articles may be divided into sections and subsections, but the length limit provided by the \corg\ should be adhered to.
-
-\subsection{Acknowledgments}
-Authors wishing to acknowledge assistance or encouragement from 
-colleagues, special work by technical staff or financial support from 
-organizations should do so in an unnumbered Acknowledgments section 
-immediately following the last numbered section of the paper. The 
-command \verb"\ack" sets the acknowledgments heading as an unnumbered
-section.
-
-\subsection{Appendices}
-Technical detail that it is necessary to include, but that interrupts 
-the flow of the article, may be consigned to an appendix. 
-Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
-If there are two or more appendices they will be called Appendix A, Appendix B, etc. 
-Numbered equations will be in the form (A.1), (A.2), etc,
-figures will appear as figure A1, figure B1, etc and tables as table A1,
-table B1, etc.
-
-The command \verb"\appendix" is used to signify the start of the
-appendixes. Thereafter \verb"\section", \verb"\subsection", etc, will 
-give headings appropriate for an appendix. To obtain a simple heading of 
-`Appendix' use the code \verb"\section*{Appendix}". If it contains
-numbered equations, figures or tables the command \verb"\appendix" should
-precede it and \verb"\setcounter{section}{1}" must follow it.
 
 \section{References}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the online version of \jpcs\ references will be linked to their original source or to the article within a secondary service such as INSPEC or ChemPort wherever possible.
-To facilitate this linking extra care should be taken when preparing reference lists.
-
-Two different styles of referencing are in common use: the Harvard alphabetical system and the Vancouver numerical system.
-For \jpcs, the Vancouver numerical system is preferred but authors should use the Harvard alphabetical system if they wish to do so.
-In the numerical system references are numbered sequentially throughout the text within square brackets, like this [2], and one number can be used to designate several references.
 
@@
 We highly recommend the {\ttfamily\textbf\selectfont iopart-num} \BibTeX\ package by Mark~A~Caprio \cite{iopartnum}, which is included with this documentation.
-
-\subsection{Reference lists}
-A complete reference should provide the reader with enough information to locate the article concerned, whether published in print or electronic form, and should, depending on the type of reference, consist of:
-
-\begin{itemize}
-\item name(s) and initials;
-\item date published;
-\item title of journal, book or other publication; 
-\item titles of journal articles may also be included (optional);
-\item volume number;
-\item editors, if any;
-\item town of publication and publisher in parentheses for {\it books};
-\item the page numbers.
-\end{itemize}
-
-Up to ten authors may be given in a particular reference; where 
-there are more than ten only the first should be given followed by 
-`{\it et al}'. If an author is unsure of a particular journal's abbreviated title it is best to leave the title in 
-full. The terms {\it loc.\ cit.\ }and {\it ibid.\ }should not be used. 
-Unpublished conferences and reports should generally not be included 
-in the reference list and articles in the course of publication should 
-be entered only if the journal of publication is known. 
-A thesis submitted for a higher degree may be included 
-in the reference list if it has not been superseded by a published 
-paper and is available through a library; sufficient information 
-should be given for it to be traced readily.
-
-\subsection{Formatting reference lists}
-Numeric reference lists should contain the references within an unnumbered section (such as \verb"\section*{References}"). The 
-reference list itself is started by the code 
-\verb"\begin{thebibliography}{<num>}", where \verb"<num>" is the largest
-number in the reference list and is completed by
-\verb"\end{thebibliography}". 
-Each reference starts with \verb"\bibitem{<label>}", where `label' is the label used for cross-referencing.
-Each \verb"\bibitem" should only contain a reference to a single article (or a single article and a preprint reference to the same article).
-When one number actually covers a group of two or more references to different articles, \verb"\nonum"
-should replace \verb"\bibitem{<label>}" at
-the start of each reference in the group after the first.
-
-For an alphabetic reference list use \verb"\begin{thereferences}" ... \verb"\end{thereferences}" instead of the
-`thebibliography' environment and each reference can be start with just \verb"\item" instead of \verb"\bibitem{label}"
-as cross referencing is less useful for alphabetic references.
-
-\subsection {References to printed journal articles}
-A normal reference to a journal article contains three changes of font (see table \ref{jfonts}) and is constructed as follows:
-
-\begin{itemize}
-\item the authors should be in the form surname (with only the first letter capitalized) followed by the initials with no periods after the initials.
-Authors should be separated by a comma except for the last two which should be separated by `and' with no comma preceding it;
-\item the article title (if given) should be in lower case letters, except for an initial capital, and should follow the date;
-\item the journal title is in italic and is abbreviated.
-If a journal has several parts denoted by different letters the part letter should be inserted after the journal in Roman type, e.g.
-{\it Phys.
-Rev.} A;
-\item the volume number should be in bold type;
-\item both the initial and final page numbers should be given where possible.
-The final page number should be in the shortest possible form and separated from the initial page number by an en rule `-- ', e.g.
-1203--14, i.e.
-the numbers `12' are not repeated.
-\end{itemize}
-
-A typical (numerical) reference list might begin
-
-\medskip
-\begin{thebibliography}{9}
-\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
-\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
-{\it J. Appl. Phys}. {\bf 87} 965 
-\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
-and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
-\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
-{\it Electron. Lett.} {\bf 32} 1105 
-\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
-{\it J. Appl. Phys.} {\bf 83} 826 
-\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
-\end{thebibliography}
-\smallskip
-
-\noindent which would be obtained by typing
-
-\begin{verbatim}
-\begin{\thebibliography}{9}
-\item Strite S and Morkoc H 1992 {\it J. Vac. Sci. Technol.} B {\bf 10} 1237 
-\item Jain S C, Willander M, Narayan J and van Overstraeten R 2000 
-{\it J. Appl. Phys}. {\bf 87} 965 
-\item Nakamura S, Senoh M, Nagahama S, Iwase N, Yamada T, Matsushita T, Kiyoku H 
-and 	Sugimoto Y 1996 {\it Japan. J. Appl. Phys.} {\bf 35} L74 
-\item Akasaki I, Sota S, Sakai H, Tanaka T, Koike M and Amano H 1996 
-{\it Electron. Lett.} {\bf 32} 1105 
-\item O'Leary S K, Foutz B E, Shur M S, Bhapkar U V and Eastman L F 1998 
-{\it J. Appl. Phys.} {\bf 83} 826 
-\item Jenkins D W and Dow J D 1989 {\it Phys. Rev.} B {\bf 39} 3317 
-\end{\thebibliography}
-\end{verbatim}
-
-\begin{center}
-\begin{table}[h]
-\centering
-\caption{\label{jfonts}Font styles for a reference to a journal article.} 
-\begin{tabular}{@{}l*{15}{l}}
-\br
-Element&Style\\
-\mr
-Authors&Roman type\\
-Date&Roman type\\
-Article title (optional)&Roman type\\
-Journal title&Italic type\\
-Volume number&Bold type\\
-Page numbers&Roman type\\
-\br
-\end{tabular}
-\end{table}
-\end{center}
-
-\subsection{References to \jpcs\ articles}
-Each conference proceeding published in \jpcs\ will be a separate {\it volume}; 
-references should follow the style for conventional printed journals. For example:\vspace{6pt}
-\numrefs{1}
-\item Douglas G 2004 \textit{J. Phys.: Conf. Series} \textbf{1} 23--36
-\endnumrefs
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{References to preprints}
-For preprints there are two distinct cases:
-\renewcommand{\theenumi}{\arabic{enumi}}
-\begin{enumerate}
-\item Where the article has been published in a journal and the preprint is supplementary reference information. In this case it should be presented as:
-\medskip
-\numrefs{1}
-\item Kunze K 2003 T-duality and Penrose limits of spatially homogeneous and inhomogeneous cosmologies {\it Phys. Rev.} D {\bf 68} 063517 ({\it Preprint} gr-qc/0303038)
-\endnumrefs
-\item Where the only reference available is the preprint. In this case it should be presented as
-\medskip
-\numrefs{1}
-\item Milson R, Coley A, Pravda V and Pravdova A 2004 Alignment and algebraically special tensors {\it Preprint} gr-qc/0401010
-\endnumrefs
-\end{enumerate}
-
-\subsection{References to electronic-only journals}
-In general article numbers are given, and no page ranges, as most electronic-only journals start each article on page 1.
-
-\begin{itemize} 
-\item For {\it New Journal of Physics} (article number may have from one to three digits)
-\numrefs{1}
-\item Fischer R 2004 Bayesian group analysis of plasma-enhanced chemical vapour deposition data {\it New. J. Phys.} {\bf 6} 25 
-\endnumrefs
-\item For SISSA journals the volume is divided into monthly issues and these form part of the article number
-
-\numrefs{2}
-\item Horowitz G T and Maldacena J 2004 The black hole final state {\it J. High Energy Phys.}  	JHEP02(2004)008
-\item Bentivegna E, Bonanno A and Reuter M 2004 Confronting the IR fixed point cosmology 	with 	high-redshift observations {\it J. Cosmol. Astropart. Phys.} JCAP01(2004)001  
-\endnumrefs
-\end{itemize}
-
-\subsection{References to books, conference proceedings and reports}
-References to books, proceedings and reports are similar to journal references, but have 
-only two changes of font (see table~\ref{book}).
-
-\begin{table}
-\centering
-\caption{\label{book}Font styles for references to books, conference proceedings and reports.}
-\begin{tabular}{@{}l*{15}{l}}
-\br
-Element&Style\\
-\mr
-Authors&Roman type\\
-Date&Roman type\\
-Book title (optional)&Italic type\\
-Editors&Roman type\\
-Place (city, town etc) of publication&Roman type\\
-Publisher&Roman type\\
-Volume&Roman type\\
-Page numbers&Roman type\\
-\br
-\end{tabular}
-\end{table}
-
-Points to note are:
-\medskip
-\begin{itemize}
-\item Book titles are in italic and should be spelt out in full with initial capital letters for all except minor words.
-Words such as Proceedings, Symposium, International, Conference, Second, etc should be abbreviated to {\it Proc.}, {\it Symp.}, {\it Int.}, {\it Conf.}, {\it 2nd}, respectively, but the rest of the title should be given in full, followed by the date of the conference and the town or city where the conference was held.
-For Laboratory Reports the Laboratory should be spelt out wherever possible, e.g.
-{\it Argonne National Laboratory Report}.
-\item The volume number, for example vol 2, should be followed by the editors, if any, in a form such as `ed A J Smith and P R Jones'.
-Use {\it et al} if there are more than two editors.
-Next comes the town of publication and publisher, within brackets and separated by a colon, and finally the page numbers preceded by p if only one number is given or pp if both the initial and final numbers are given.
-\end{itemize}
-
-Examples taken from published papers:
-\medskip
-
-\numrefs{99}
-\item Kurata M 1982 {\it Numerical Analysis for Semiconductor Devices} (Lexington, MA: Heath)
-\item Selberherr S 1984 {\it Analysis and Simulation of Semiconductor Devices} (Berlin: Springer)
-\item Sze S M 1969 {\it Physics of Semiconductor Devices} (New York: Wiley-Interscience)
-\item Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} (Moscow: Moscow State University Press) p 103
-\item Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear Physics (Munich)} vol 1 (Amsterdam: 	North-Holland/American Elsevier) p 517
-\item Cheng G X 2001 {\it Raman and Brillouin Scattering-Principles and Applications} (Beijing: Scientific) 
-\item Szytula A and Leciejewicz J 1989 {\it Handbook on the Physics and Chemistry of Rare Earths} vol 12, ed K A Gschneidner Jr and L Erwin (Amsterdam: Elsevier) p 133
-\item Kuhn T 1998 {\it Density matrix theory of coherent ultrafast dynamics Theory of Transport Properties of Semiconductor Nanostructures} (Electronic Materials vol 4) ed E Sch\"oll (London: Chapman and Hall) chapter 6 pp 173--214
-\endnumrefs
-
-\section{Tables and table captions}
-Tables should be numbered serially and referred to in the text 
-by number (table 1, etc, {\bf rather than} tab.
-1).
-Each table should be a float and be positioned within the text at the most convenient place near to where it is first mentioned in the text.
-It should have an
-explanatory caption which should be as concise as possible.
-
-\subsection{The basic table format}
-The standard form for a table is:
-\begin{verbatim}
-\begin{table}
-\caption{\label{label}Table caption.}
-\begin{center}
-\begin{tabular}{llll}
-\br
-Head 1&Head 2&Head 3&Head 4\\
-\mr
-1.1&1.2&1.3&1.4\\
-2.1&2.2&2.3&2.4\\
-\br
-\end{tabular}
-\end{center}
-\end{table}
-\end{verbatim}
-
-The above code produces table~\ref{ex}.
-
-\begin{table}[h]
-\caption{\label{ex}Table caption.}
-\begin{center}
-\begin{tabular}{llll}
-\br
-Head 1&Head 2&Head 3&Head 4\\
-\mr
-1.1&1.2&1.3&1.4\\
-2.1&2.2&2.3&2.4\\
-\br
-\end{tabular}
-\end{center}
-\end{table}
-
-Points to note are:
-\medskip
-\begin{enumerate}
-\item The caption comes before the table.
-\item The normal style is for tables to be centred in the same way as
-equations. This is accomplished
-by using \verb"\begin{center}" \dots\ \verb"\end{center}".
-
-\item The default alignment of columns should be aligned left.
-
-\item Tables should have only horizontal rules and no vertical ones. The rules at
-the top and bottom are thicker than internal rules and are set with
-\verb"\br" (bold rule). 
-The rule separating the headings from the entries is set with
-\verb"\mr" (medium rule). These commands do not need a following double backslash.
-
-\item Numbers in columns should be aligned as appropriate, usually on the decimal point;
-to help do this a control sequence \verb"\lineup" has been defined 
-which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
-to be a space the width of a minus sign, and \verb"\-" to be a left
-overlapping minus sign. \verb"\-" is for use in text mode while the other
-two commands may be used in maths or text.
-(\verb"\lineup" should only be used within a table
-environment after the caption so that \verb"\-" has its normal meaning
-elsewhere.) See table~\ref{tabone} for an example of a table where
-\verb"\lineup" has been used.
-\end{enumerate}
-
-\begin{table}[h]
-\caption{\label{tabone}A simple example produced using the standard table commands 
-and $\backslash${\tt lineup} to assist in aligning columns on the 
-decimal point. The width of the 
-table and rules is set automatically by the 
-preamble.}
-
-\begin{center}
-\lineup
-\begin{tabular}{*{7}{l}}
-\br                              
-$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
-\mr
-\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
-\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
-\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
-3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
-\br
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Figures and figure captions}
-Figures must be included in the source code of an article at the appropriate place in the text not grouped together at the end.
-
-Each figure should have a brief caption describing it and, if 
-necessary, interpreting the various lines and symbols on the figure. 
-As much lettering as possible should be removed from the figure itself and 
-included in the caption. If a figure has parts, these should be 
-labelled ($a$), ($b$), ($c$), etc. 
-\Tref{blobs} gives the definitions for describing symbols and lines often
-used within figure captions (more symbols are available
-when using the optional packages loading the AMS extension fonts).
-
-\begin{table}[h]
-\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
-captions.}
-\begin{center}
-\begin{tabular}{lllll}
-\br
-Control sequence&Output&&Control sequence&Output\\
-\mr
-\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
-\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
-\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
-\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
-\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
-\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
-\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
-\br
-\end{tabular}
-\end{center}
-\end{table}
-
-Authors should try and use the space allocated to them as economically as possible.
-At times it may be convenient to put two figures side by side or the caption at the side of a figure.
-To put figures side by side, within a figure environment, put each figure and its caption into a minipage with an appropriate width (e.g.
-3in or 18pc if the figures are of equal size) and then separate the figures slightly by adding some horizontal space between the two minipages (e.g.
-\verb"\hspace{.2in}" or \verb"\hspace{1.5pc}".
-To get the caption at the side of the figure add the small horizontal space after the \verb"\includegraphics" command and then put the \verb"\caption" within a minipage of the appropriate width aligned bottom, i.e.
-\verb"\begin{minipage}[b]{3in}" etc (see code in this file used to generate figures 1--3).
-
-Note that it may be necessary to adjust the size of the figures (using optional arguments to \verb"\includegraphics", for instance \verb"[width=3in]") to get you article to fit within your page allowance or to obtain good page breaks.
 

### 2015-09-07 paper.tex
added geom plot

@@
 \begin{abstract}Changing the configuration of the cold neutron source during an extended shutdown of Swiss Spallation Neutron Source (SINQ) is being considered for improving performance of the instruments that use the cold source.
-The cold neutron source consists of a 20 L volume of liquid D2 at approximately 25 K.
-Previous upgrades included adding a re-entrant hole into one side of the D2 volume to allow cold neutrons to stream uninhibited from the center of the source towards the instrument neutron guides.
+The cold neutron source consists of a 20 L volume of liquid D$_2$ at approximately 25 K.
+Previous upgrades included adding a re-entrant hole into one side of the D$_2$ volume to allow cold neutrons to stream uninhibited from the center of the source towards the instrument neutron guides.
 Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.6, with gains increasing with wavelength.
 These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided.
-Voiding the re-entrant hole relies on radiative heating to boil D2 which in turn fills the re-entrant hole cavity, pushing the liquid D2 out.
-Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D2), removing some extra structural material around the D2 tank, redesigning the re-entrant hole geometry to be more optically ideal, introducing a Pb-208 reflector to minimize cold neutron up-scattering from the surrounding D2O moderator tank, and implementing a small liquid H2 volume to provide a cold neutron “hot spot” for certain instruments.
+Voiding the re-entrant hole relies on radiative heating to boil D$_2$ which in turn fills the re-entrant hole cavity, pushing the liquid D$_2$ out.
+Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D$_2$), removing some extra structural material around the D2 tank, redesigning the re-entrant hole geometry to be more optically ideal, introducing a Pb-208 reflector to minimize cold neutron up-scattering from the surrounding D$_2$O moderator tank, and implementing a small liquid H$_2$ volume to provide a cold neutron “hot spot” for certain instruments.
 These changes are predicted to increase neutron fluence between 1.1 to 2.0 times the current levels, depending on instrument location, view, and wavelengths of interest.
@@
 
-\section{Preparing your paper}
+There is a planned shutdown of the Swiss Spallation Neutron Source (SINQ) in 2017, which provides an opportunity for changes to be made to the liquid deuterium cold neutron source.
+The 20 liter volume of liquid D$_2$ at approximately 25 K is located within the D$_2$O moderator tank surrounding the Pb spallation target.
+The innermost face of the cold source is approximately 35 cm away from the center of the target.
+In the planned upgrade strategies, no changes to the surrounding aluminium and zirconium safety hulls will be made, and no changes to the insert tube structure will be made.
+I.e., all changes must fit into the existing multi-walled insert geometry.
 
-\section{The title, authors, addresses and abstract}
+\section{Re-entrant Hole}
 
-\subsection{Sample coding for the start of an article}
+The goal of the re-entrant hole (REH) is to remove scattering and absorbing material between the cold neutron maximum and the direction of interest.
+In this case, the cold neutron maximum is at the center of the cold source and the direciton of interest is towards the SINQ guide hall.
 
-\section{The text}
+Voiding the re-entrant hole relies on radiative heating to boil D$_2$ which in turn fills the re-entrant hole cavity, pushing the liquid D$_2$ out.
+Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D$_2$)
+
+Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.6, with gains increasing with wavelength.
+These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided.
+All future designs will have an external REH, which will decouple the fill level from radiation heating and ensure that the REH is never filled with liquid D$_2$.
+
+\section{Simulation Geometry}
+
+\begin{figure}
+\begin{center}
+\includegraphics[trim={9.2cm 8cm 4cm 8cm},clip]{graphics/geom.pdf}
+\end{center}
+\caption{\label{geom}A horizontal slice through the MCNP simulation geometry showing the target (magenta), moderator tank (blue_, cold source (purple), nozzle (pink), and neutron guide entrance (grey with circle).}
+\end{figure}
+
+plot of geom, mention variance reduction
+
+\section{Neutron Guide Response}
+
+\subsection{Guide Reflectivity}
+
+model
+guide parameters
+stability issues
+
+\cite{mcnpx_reflectivity}
+
+\subsection{Reconstruction}
+
+method for entry
+plot of transfer curves and/or contour plot
+
+\subsection{Self-Consistency Test}
+
+plot of benchmark
+
+\section{REH Parametric Study in the Horizontal Plane}
+
+\subsection{Parameters}
+
+plot of reh and angles
+summary of cases
+
+\subsection{Study Results}
+
+plot of spectral band
+plot of geometry in XY
+
+\section{Conculsions}
+
+28\% is great
+
+\section{Future Work}
+
+all that jazz
 
@@
 
-Using the graphicx package figures can be included using code such as:
-\begin{verbatim}
-\begin{figure}
-\begin{center}
-\includegraphics{file.eps}
-\end{center}
-\caption{\label{label}Figure caption}
-\end{figure}
-\end{verbatim}
-
 \section*{References}

### 2015-09-08 paper.tex
added geom plot
more

@@
 
+Figure \ref{geom} shows a zoomed-in view of the important parts of the MCNP model geometry.
+A CAD model of the neutron guide bundles was converted to MCNP geometry by the MCAM software from XXX university in XXX China and integrated into the model \cite{mcam}.
+The target is made of Pb rods with zircalloy cladding and is cooled by D$_2$O, the moderator tank is filled with D$_2$O, the cold source is liquid D$_2$, the nozzles with a low-pressure helium mixture, and the shielding and neutron guide structure is steel.
+All structural material in the moderator tank is AlMg3, which is shown in yellow in Figure \ref{geom}.
+
 \begin{figure}
@@
 \end{center}
-\caption{\label{geom}A horizontal slice through the MCNP simulation geometry showing the target (magenta), moderator tank (blue_, cold source (purple), nozzle (pink), and neutron guide entrance (grey with circle).}
+\caption{\label{geom}A horizontal slice through the MCNP simulation geometry showing the target (magenta), moderator tank (blue), cold source (purple), nozzle (pink), and neutron guide entrance (grey with circle).}
 \end{figure}
 
-plot of geom, mention variance reduction
+\section{Variance Reduction}
+
+Two variance reduciton methods were used in conjunction in order to perform the calculations in a reasonable amount of time.
+First, mesh-based weight windows were generated based on the response of a point detector located 75 cm from the neutron guide entrance.
+These windows serve to increase the number of neutrons that scatter inside the cold source while preserving the mean particle weight of an analog simulation by casusing the neutrons in the moderator tank to carry a higher weight then be split into many lower-weight particles when they enter the cold source volume.
+
+The second variance reduction method used is a ``DXTRAN'' sphere.
+This tool is a non-physical sphere that is placed around the guide entrance that causes neutrons to be generated on its surface.
+Whenever a neutron undergoes a scattering reaction, the probability of scattering into the sphere's direction is calculated, a line is traced from the scattering location to the sphere's surface, and a neutron is generated there with a weight reduced by the scattering probability and the optical thickness of the medium in between.
+The generated neutrons are then transported normally inside the sphere \cite{mcnp}.
+This method served to preferentially scatter neutrons into the direction of the neutron guide.
 
 \section{Neutron Guide Response}
+
+In conjunction with the variance reduction methods described in the previous section, an approximation to how the neutron geuides transport neutrons was also used.
 

### 2015-09-08 paper.tex
more

@@
 In conjunction with the variance reduction methods described in the previous section, an approximation to how the neutron geuides transport neutrons was also used.
+A patch was developed at ORNL and PSI that implements the McStas guide reflectivity model in MCNPX 2.5.0 and 2.7.0 \cite{mcnp_reflectivity, EK_reflectivity}, but the model is analog and is not fully compatible with DXTRAN spheres.
+The implmentation is analog in the sense that if a neutron is sampled to \emph{not} reflect on a guide surface, it is transmitted into the next cell.
+This means that neutron paths have to be sampled multiple times to account for any reflectivity losses, which slows the simulation down.
+
+Also, some stability issues were encountered while using the reflectivtity patch in conjunction with the DXTRAN sphere.
+In order to ensure stable runs, a simulation was done first where a surface source was written at the guide entrance surface where any neutrons entering the guide were recorded and terminated.
+This source was used in a second simulation with the guide reflecitvity turned on and used to transport the entering neutrons to the end of the guide where a tally was scored.
+Again, this process slowed the simulation down and made studies with many cases more difficult.
+An approximaiton to the guide response was used to eliminate the need for a second run to simply get the neutrons to the end of the guide.
 
@@
 guide parameters
-stability issues
 

### 2015-09-08 paper.tex
reflectivity graphics

@@
 \documentclass[a4paper]{jpconf}
-\usepackage{graphicx}
+\usepackage{graphicx,amsmath}
 \begin{document}
@@
 
-model
-guide parameters
+The guide reflectivity model implmented in MCNP is identical to that used in McStas.
+The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity}, along with the reflectivity equation and parameter values shown in Eq.
+\ref{eq:ref}.
+
+\begin{figure}[h]
+\begin{minipage}{14pc}
+\includegraphics[scale=.4]{graphics/refl.pdf}
+\caption{\label{SINQ_reflectivity} The reflectivity curve of the current SINQ neutron guides.}
+\end{minipage}\hspace{5pc}%
+\begin{minipage}{11pc}
+\begin{multline}\label{eq:ref}\scriptsize
+R(Q) = 
+\begin{cases}
+    \mbox{if } Q > Q_c : \\
+    \frac{R_0}{2}\left\{  1 - \tanh\left(  \frac{Q - m Q_c}{W}\right) \right\}\{1-\alpha(Q-Q_c)\} \\
+    \\
+    \mbox{if } Q \leq Q_c :\\
+    R_0 \\
+\end{cases} \\ \\ 
+\begin{tabular}{c c c}
+$R_0=0.995$ & $Q_c=2.17\times10^{-2}\AA^{-1}$ & $m=3.6$ \\ 
+$\alpha=3.99 \AA$ & $W=10^{-3} \AA^{-1}$ 
+\end{tabular}
+\end{multline}
+\end{minipage} 
+\end{figure}
 

### 2015-09-08 paper.tex
reflectivity graphics
xfer benchmark

@@
 The guide reflectivity model implmented in MCNP is identical to that used in McStas.
-The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity}, along with the reflectivity equation and parameter values shown in Eq.
+The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity} andh the reflectivity equation and parameter values shown in Eq.
 \ref{eq:ref}.
+The values shown are the same for all the guides in the SINQ hall \cite{SINQ_guide_values}.
 
@@
     R_0 \\
-\end{cases} \\ \\ 
+\end{cases} \\ \\ \\
 \begin{tabular}{c c c}
-$R_0=0.995$ & $Q_c=2.17\times10^{-2}\AA^{-1}$ & $m=3.6$ \\ 
-$\alpha=3.99 \AA$ & $W=10^{-3} \AA^{-1}$ 
-\end{tabular}
+$R_0=0.995$ & $Q_c=2.17\times10^{-2}\AA^{-1}$ & $m=1.9$ \\ 
+$\alpha=6.40 \AA$ & $W=4.0\times10^{-3} \AA^{-1}$ 
+\end{tabular} \\
 \end{multline}
@@
 
-\cite{mcnpx_reflectivity}
+Since the neutron reflection probability is based on momentum transfer and the reflections are specular, it is determined by the incident neutron angle and energy.
+If the guide is rectangular, the reflection probability will not change as the neutron travels down the guide since the reflection angle will remain constant.
+These conditions mean that the exiting neutron current should be compleltely defined by the incident polar angle and energy of a neutron entering the guide.
+The position in the guide entrance will determine the phase of the exiting rays, but if the entire exit surface is summed over, this phase becomes irrelevant.
 
@@
 
-method for entry
-plot of transfer curves and/or contour plot
+In order to approximate the neutron current exiting the guide, a number of fixed-source runs of MCNPX were done as precalculations to the parametric study.
+An evenly-distributed source was defined at the entrance surface of the guide that emits neutrons in a polar angle bin $1/8^\circ$ wide and logarithmically in energy (to ensure low energies are sampled fairly).
+The exiting current at the end of the guide was tallied and divided by the entrance current to yield a transfer function in energy for the polar angle of the source.
+This was done for $0-7.5^\circ$ of polar angle to yield the set of 60 functions shown in figure \ref{xfer_func}.
+
+%trim <left> <lower> <right> <upper>
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.3,trim={2cm 1.7cm 2cm 0.8cm},clip]{graphics/xfer_func.pdf}
+\end{center}
+\caption{\label{xfer_func}Set of transfer functions for a m=2 guide.}
+\end{figure}
+
+If neutrons are tallied at the guide entrance in the same polar and energy binning as the transfer funcitons, it can be multiplied by the set and summed over all incident angles to yield the integrated neutron spectrum at the guide exit.
 
@@
 
-plot of benchmark
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{graphics/xfer_bench.pdf}
+\end{center}
+\caption{\label{xfer_bench}Set of transfer functions for a m=2 guide.}
+\end{figure}
 

### 2015-09-08 paper.tex
adding results

@@
 This was done for $0-7.5^\circ$ of polar angle to yield the set of 60 functions shown in figure \ref{xfer_func}.
+The colors mean????
 
@@
 If neutrons are tallied at the guide entrance in the same polar and energy binning as the transfer funcitons, it can be multiplied by the set and summed over all incident angles to yield the integrated neutron spectrum at the guide exit.
+This way, the reflectivity model can be eliminated from the transport runs and a good estimate of the exiting current can still be made.
 
 \subsection{Self-Consistency Test}
+
+In order to verify that the reconstruction method works as expected, a comparison to the spectrum calculated by the explicit model was made.
+As mentioned previously, a surface source was written at the guide entrance, then this was used as the source for a second run with the guide reflectivity activiated.
+During this run, the entry and exit current was tallied.
+The entry current was binning in polar angle according to the divisions in the pre-calculated transfer functions.
+The results of the comparison are shown in Figure \ref{xfer_bench}.
+The green line is the integrated neutron spectrum at the guide entrance, the blue line is the integrated exit current that was tallied at the guide exit, and the red curve is the exit spectrum calculated by multiplying the entrance spectrum by the transfer functions (and then summing them).
+The maximum error seen is about XXX\%, and decreases with energy, and has a 1-norm value of XXX\%.
 
@@
 
-\subsection{Parameters}
+The re-entrant hole parametric study was done to investigate a wide range of geometries in the horizonal plane, where the guide width is smaller than the hole size.
+Four REH depths (114, 10, 6, 2 cm), four opening widths (4, 8, 12, 16 cm), and eleven hole slopes (-0.5, -0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5) were investigated in the study for a total of 176 cases.
+Figure \ref{parametric_geom} shows the parameters in relation to the cold source geometry.
 
-plot of reh and angles
-summary of cases
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{graphics/xfer_bench.pdf}
+\end{center}
+\caption{\label{parametric_geom}The geometry varied in the REH parametric study.}
+\end{figure}
 
-\subsection{Study Results}
+plot of spectral band, FOM is
 
-plot of spectral band
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.38,trim={1cm 2.35cm 1cm 0cm},clip]{graphics/parametric_REH.pdf}
+\end{center}
+\caption{\label{parametric_REH}The envelope formed by the spectra from all 176 cases considered (upper) and their figures of merit (lower) which is total current from 3 to 6 \AA.}
+\end{figure}
+
 plot of geometry in XY
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.6,trim={11.2cm 8cm 5cm 3cm},clip]{graphics/case077.pdf}
+\end{center}
+\caption{\label{case077}The best-performing horizontal geometry for the REH.}
+\end{figure}
 
@@
 
-\begin{figure}[h]
-\begin{minipage}{14pc}
-\includegraphics[width=14pc]{name.eps}
-\caption{\label{label}Figure caption for first of two sided figures.}
-\end{minipage}\hspace{2pc}%
-\begin{minipage}{14pc}
-\includegraphics[width=14pc]{name.eps}
-\caption{\label{label}Figure caption for second of two sided figures.}
-\end{minipage} 
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=14pc]{name.eps}\hspace{2pc}%
-\begin{minipage}[b]{14pc}\caption{\label{label}Figure caption for a narrow figure where the caption is put at the side of the figure.}
-\end{minipage}
-\end{figure}
-
-\section*{References}
-\begin{thebibliography}{9}
-\bibitem{iopartnum} IOP Publishing is to grateful Mark A Caprio, Center for Theoretical Physics, Yale University, for permission to include the {\tt iopart-num} \BibTeX package (version 2.0, December 21, 2006) with  this documentation.
-Updates and new releases of {\tt iopart-num} can be found on \verb"www.ctan.org" (CTAN).
-\end{thebibliography}
-
 \end{document}

### 2015-09-08 paper.tex
adding results

@@
 
-plot of spectral band, FOM is
+With all of the variance reduciton and approximations implmented, each case takes about one hours to run.
+The spectra from all the casesa are shown in upper plot in Figure \ref{parametric_REH}, and the figure of merit of each case is shown in the lower plot.
+The figure of merit was simply chosen to be the total current exiting the guide from 3 to 6 \AA.
+The perfomance is
 
@@
 
-plot of geometry in XY
+The geometry of the best-performing case is shown in figure \ref{case077}.
 

### 2015-09-09 paper.tex
more results

--- 2015-09-08 paper.tex
@@
 The re-entrant hole parametric study was done to investigate a wide range of geometries in the horizonal plane, where the guide width is smaller than the hole size.
-Four REH depths (114, 10, 6, 2 cm), four opening widths (4, 8, 12, 16 cm), and eleven hole slopes (-0.5, -0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5) were investigated in the study for a total of 176 cases.
+Four REH depths (14, 10, 6, 2 cm), four opening widths (4, 8, 12, 16 cm), and eleven hole slopes (-0.5, -0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5) were investigated in the study for a total of 176 cases.
 Figure \ref{parametric_geom} shows the parameters in relation to the cold source geometry.
+The REH vertical dimensions were chosen to be the full width of the nozzle with a slight tapering slope inward.
+The vertical dimensions were kept constant in this study, but will be the focus of future work.
 
@@
 \begin{center}
-\includegraphics[scale=0.4]{graphics/xfer_bench.pdf}
+\includegraphics[scale=0.4,trim={13cm 6cm 4cm 5cm},clip]{graphics/para_geom.pdf}
 \end{center}
-\caption{\label{parametric_geom}The geometry varied in the REH parametric study.}
+\caption{\label{parametric_geom}The geometry varied in the REH parametric study. ``A'' is the hole depth, ``B'' is the opening width, and ``C'' is the hole slope.}
 \end{figure}
 
-plot of spectral band, FOM is
+With all of the variance reduciton and approximations implmented, each case took about one hour to run on the PSI cluster.
+The spectra from all the cases are shown in upper plot in Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
+The figure of merit was chosen to be the total current exiting the guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall.
+The performance is
 
@@
 \end{center}
-\caption{\label{parametric_REH}The envelope formed by the spectra from all 176 cases considered (upper) and their figures of merit (lower) which is total current from 3 to 6 \AA.}
+\caption{\label{parametric_REH}The envelope formed by the spectra from all 176 cases considered (upper) and their figures of merit (lower) which is total current from 3 to 6 \AA{}.}
 \end{figure}
 
-plot of geometry in XY
+The geometry of the best-performing case is shown in figure \ref{case077}.
+The depth is 10 cm, the opening width is 12 cm, and the slope is 0.5.
+This opening is as wide as the nozzle and almost tapers to a point at the maximum depth.
+The maximum depth is 4 cm from the cold source geometrical center.
 
@@
 
+Figure \ref{parametric_gain} shows the gain from the best performaning REH geometry over an absent REH.
+The maximum gain 1.32 at 5.5 \AA{} and its average value from 3-6 \AA{} is 1.25.
+Similar gains should be seen by all instruments in the SINQ guide hall.
+The drop in gain after 5.5 \AA{} is suspected to be from the liquid D$_2$ cross section dropping from about 5.5 to 25 \AA{}, making it more transparent to colder neutrons and reducing the re-entrant hole's benefits.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.38,trim={0cm 0cm 0cm 0cm},clip]{graphics/parametric_gain.pdf}
+\end{center}
+\caption{\label{parametric_gain}The gain factor of the neutron guide exit current of best-performing REH geometry over the REH being absent.}
+\end{figure}
+
 \section{Conculsions}
 
-28\% is great
+Flux reconstruction method verified  to be at least self-consistent
+Near optimal X-Y REH geometry has been determined
+REH increases total exit current by 1.25\% on average from 3-6 \AA{} with a peak gain of 1.32 at 5.5 \AA{}.
 
@@
 
-all that jazz
+Need to investigate REH sensitivity to vertical changes
+Smaller study to determine exact dimensions
+Extend D2 volume instead of Pb-208 reflector
+H2 cold spots
+Affect on non-REH side
+Make switch in MCNP reflectivity patch to reduce weight instead of leaking unreflected neutrons
 

### 2015-09-09 paper.tex
more results

@@
 \end{center}
-\caption{\label{xfer_bench}Set of transfer functions for a m=2 guide.}
+\caption{\label{xfer_bench}The reconstructed guide exit current compared to the exit current calculated with a MCNP simulation with guide reflectivity activated.}
 \end{figure}
@@
 
-\begin{figure}
+\begin{figure}[h]
+\begin{minipage}{14pc}
 \begin{center}
@@
 \caption{\label{parametric_geom}The geometry varied in the REH parametric study. ``A'' is the hole depth, ``B'' is the opening width, and ``C'' is the hole slope.}
+\end{minipage}\hspace{5pc}%
+\begin{minipage}{11pc}
+\begin{center}
+\includegraphics[scale=0.4,trim={11.2cm 8cm 5cm 3cm},clip]{graphics/case077.pdf}
+\end{center}
+\caption{\label{case077}The best-performing horizontal geometry for the REH.}
+\end{minipage} 
 \end{figure}
 
-With all of the variance reduciton and approximations implmented, each case took about one hour to run on the PSI cluster.
+With all of the variance reduciton and approximations implemented, each case took about one hour to run on a 144-core configuration on a computer cluster at PSI.
 The spectra from all the cases are shown in upper plot in Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
 The figure of merit was chosen to be the total current exiting the guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall.
-The performance is
+The parameters were varied in slope-width-depth order, with slope being the fasted varied parameter.
+Figure \ref{parametric_REH} has labeled, colored blocks in the lower plot to show which parameters are constant for that block.
+Slope and opening width have the most affect on performance at large depths.
+
+The geometry of the best-performing case is shown in figure \ref{case077}.
+The depth is 10 cm, the opening width is 12 cm, and the slope is 0.5.
+This opening is as wide as the nozzle and almost tapers to a point at the maximum depth.
+The maximum depth is 4 cm from the radial center of the cold source.
 
@@
 
-The geometry of the best-performing case is shown in figure \ref{case077}.
-The depth is 10 cm, the opening width is 12 cm, and the slope is 0.5.
-This opening is as wide as the nozzle and almost tapers to a point at the maximum depth.
-The maximum depth is 4 cm from the cold source geometrical center.
-
 \begin{figure}
 \begin{center}
-\includegraphics[scale=0.6,trim={11.2cm 8cm 5cm 3cm},clip]{graphics/case077.pdf}
+\includegraphics[scale=0.38,trim={0cm 0cm 0cm 0cm},clip]{graphics/parametric_gain.pdf}
 \end{center}
-\caption{\label{case077}The best-performing horizontal geometry for the REH.}
+\caption{\label{parametric_gain}The gain factor of the neutron guide exit current of best-performing REH geometry over the REH being absent.}
 \end{figure}
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.38,trim={0cm 0cm 0cm 0cm},clip]{graphics/parametric_gain.pdf}
-\end{center}
-\caption{\label{parametric_gain}The gain factor of the neutron guide exit current of best-performing REH geometry over the REH being absent.}
-\end{figure}
-
 \section{Conculsions}
 
-Flux reconstruction method verified  to be at least self-consistent
-Near optimal X-Y REH geometry has been determined
-REH increases total exit current by 1.25\% on average from 3-6 \AA{} with a peak gain of 1.32 at 5.5 \AA{}.
+From this study and the requirements it imposed on the simulation method, it can be concluded that the flux reconstruction method has been verified to be at least self-consistent, and that a near-optimal horizontal REH geometry has been determined.
+The REH increases total exit current by 1.25\% on average from 3-6 \AA{} with a peak gain of 1.32 at 5.5 \AA{}.
 

### 2015-09-09 paper.tex
more results

@@
 
-Need to investigate REH sensitivity to vertical changes
-Smaller study to determine exact dimensions
-Extend D2 volume instead of Pb-208 reflector
-H2 cold spots
-Affect on non-REH side
-Make switch in MCNP reflectivity patch to reduce weight instead of leaking unreflected neutrons
+This study has only determined the horizontla geometry of the re-entrant hole in the cold source at SINQ.
+Another study is needed to investigate REH sensitivity to vertical changes, as well as a parametric study over a smaller range near the optimal point to determine more exact dimensions.
+The affect the REH has on the neutron flux on the opposite side will also be determined.
+
+Different types of reflector materials and configurations will also be investigated.
+The refector sits behind the cold source on the side opposite the target and reducing cold neutron losses in it may increase the guide exit current.
+Adding a belt of liquid H$_2$ to produce a ``cold spot'' for focusing instruments will also be investigated.
+In these studies, the flux reconstruction method will once again be used.
+
+Futher development of the guide refelctivity patch for MCNP 6.1 will also be done.
+Specifically, making a switch to reduce neutron weight upon reflection instead of leaking non-reflected neutrons in order to speed up in-beam calculations where this signal is of interest and not the noise.
 

### 2015-09-10 paper.tex
adding references
new gain

@@
 \usepackage{graphicx,amsmath}
+\bibliographystyle{iopart-num}
+
 \begin{document}
@@
 The innermost face of the cold source is approximately 35 cm away from the center of the target.
-In the planned upgrade strategies, no changes to the surrounding aluminium and zirconium safety hulls will be made, and no changes to the insert tube structure will be made.
+In the planned upgrade strategies, no changes to the surrounding aluminum and zirconium safety hulls will be made, and no changes to the insert tube structure will be made.
 I.e., all changes must fit into the existing multi-walled insert geometry.
@@
 The goal of the re-entrant hole (REH) is to remove scattering and absorbing material between the cold neutron maximum and the direction of interest.
-In this case, the cold neutron maximum is at the center of the cold source and the direciton of interest is towards the SINQ guide hall.
+In this case, the cold neutron maximum is at the center of the cold source and the direction of interest is towards the SINQ guide hall.
 
@@
 
-Two variance reduciton methods were used in conjunction in order to perform the calculations in a reasonable amount of time.
+Two variance reduction methods were used in conjunction in order to perform the calculations in a reasonable amount of time.
 First, mesh-based weight windows were generated based on the response of a point detector located 75 cm from the neutron guide entrance.
-These windows serve to increase the number of neutrons that scatter inside the cold source while preserving the mean particle weight of an analog simulation by casusing the neutrons in the moderator tank to carry a higher weight then be split into many lower-weight particles when they enter the cold source volume.
+These windows serve to increase the number of neutrons that scatter inside the cold source while preserving the mean particle weight of an analog simulation by causing the neutrons in the moderator tank to carry a higher weight then be split into many lower-weight particles when they enter the cold source volume.
 
@@
 A patch was developed at ORNL and PSI that implements the McStas guide reflectivity model in MCNPX 2.5.0 and 2.7.0 \cite{mcnp_reflectivity, EK_reflectivity}, but the model is analog and is not fully compatible with DXTRAN spheres.
-The implmentation is analog in the sense that if a neutron is sampled to \emph{not} reflect on a guide surface, it is transmitted into the next cell.
+The implementation is analog in the sense that if a neutron is sampled to \emph{not} reflect on a guide surface, it is transmitted into the next cell.
 This means that neutron paths have to be sampled multiple times to account for any reflectivity losses, which slows the simulation down.
 
-Also, some stability issues were encountered while using the reflectivtity patch in conjunction with the DXTRAN sphere.
+Also, some stability issues were encountered while using the reflectivity patch in conjunction with the DXTRAN sphere.
 In order to ensure stable runs, a simulation was done first where a surface source was written at the guide entrance surface where any neutrons entering the guide were recorded and terminated.
-This source was used in a second simulation with the guide reflecitvity turned on and used to transport the entering neutrons to the end of the guide where a tally was scored.
+This source was used in a second simulation with the guide reflectivity turned on and used to transport the entering neutrons to the end of the guide where a tally was scored.
 Again, this process slowed the simulation down and made studies with many cases more difficult.
-An approximaiton to the guide response was used to eliminate the need for a second run to simply get the neutrons to the end of the guide.
+An approximation to the guide response was used to eliminate the need for a second run to simply get the neutrons to the end of the guide.
 
@@
 
-The guide reflectivity model implmented in MCNP is identical to that used in McStas.
-The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity} andh the reflectivity equation and parameter values shown in Eq.
+The guide reflectivity model implemented in MCNP is identical to that used in McStas.
+The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq.
 \ref{eq:ref}.
@@
 If the guide is rectangular, the reflection probability will not change as the neutron travels down the guide since the reflection angle will remain constant.
-These conditions mean that the exiting neutron current should be compleltely defined by the incident polar angle and energy of a neutron entering the guide.
+These conditions mean that the exiting neutron current should be completely defined by the incident polar angle and energy of a neutron entering the guide.
 The position in the guide entrance will determine the phase of the exiting rays, but if the entire exit surface is summed over, this phase becomes irrelevant.
@@
 
-If neutrons are tallied at the guide entrance in the same polar and energy binning as the transfer funcitons, it can be multiplied by the set and summed over all incident angles to yield the integrated neutron spectrum at the guide exit.
+If neutrons are tallied at the guide entrance in the same polar and energy binning as the transfer functions, it can be multiplied by the set and summed over all incident angles to yield the integrated neutron spectrum at the guide exit.
 This way, the reflectivity model can be eliminated from the transport runs and a good estimate of the exiting current can still be made.
@@
 In order to verify that the reconstruction method works as expected, a comparison to the spectrum calculated by the explicit model was made.
-As mentioned previously, a surface source was written at the guide entrance, then this was used as the source for a second run with the guide reflectivity activiated.
+As mentioned previously, a surface source was written at the guide entrance, then this was used as the source for a second run with the guide reflectivity activated.
 During this run, the entry and exit current was tallied.
@@
 
-The re-entrant hole parametric study was done to investigate a wide range of geometries in the horizonal plane, where the guide width is smaller than the hole size.
+The re-entrant hole parametric study was done to investigate a wide range of geometries in the horizontal plane, where the guide width is smaller than the hole size.
 Four REH depths (14, 10, 6, 2 cm), four opening widths (4, 8, 12, 16 cm), and eleven hole slopes (-0.5, -0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5) were investigated in the study for a total of 176 cases.
@@
 
-With all of the variance reduciton and approximations implemented, each case took about one hour to run on a 144-core configuration on a computer cluster at PSI.
+With all of the variance reduction and approximations implemented, each case took about one hour to run on a 144-core configuration on a computer cluster at PSI.
 The spectra from all the cases are shown in upper plot in Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
@@
 
-Figure \ref{parametric_gain} shows the gain from the best performaning REH geometry over an absent REH.
-The maximum gain 1.32 at 5.5 \AA{} and its average value from 3-6 \AA{} is 1.25.
+Figure \ref{parametric_gain} shows the gain from the best performing REH geometry over an absent REH.
+The maximum gain 1.29 at 5.5 \AA{} and its average value from 3-6 \AA{} is 1.24.
 Similar gains should be seen by all instruments in the SINQ guide hall.
@@
 From this study and the requirements it imposed on the simulation method, it can be concluded that the flux reconstruction method has been verified to be at least self-consistent, and that a near-optimal horizontal REH geometry has been determined.
-The REH increases total exit current by 1.25\% on average from 3-6 \AA{} with a peak gain of 1.32 at 5.5 \AA{}.
+The REH increases total exit current by 1.24\% on average from 3-6 \AA{} with a peak gain of 1.29 at 5.5 \AA{}.
 
@@
 
-This study has only determined the horizontla geometry of the re-entrant hole in the cold source at SINQ.
+This study has only determined the horizontal geometry of the re-entrant hole in the cold source at SINQ.
 Another study is needed to investigate REH sensitivity to vertical changes, as well as a parametric study over a smaller range near the optimal point to determine more exact dimensions.
@@
 
-Futher development of the guide refelctivity patch for MCNP 6.1 will also be done.
+Further development of the guide reflectivity patch for MCNP 6.1 will also be done.
 Specifically, making a switch to reduce neutron weight upon reflection instead of leaking non-reflected neutrons in order to speed up in-beam calculations where this signal is of interest and not the noise.
 
-\section{References}
-
-\subsection{Using \BibTeX}
-We highly recommend the {\ttfamily\textbf\selectfont iopart-num} \BibTeX\ package by Mark~A~Caprio \cite{iopartnum}, which is included with this documentation.
+\section*{References}
+\bibliography{paper}
 

### 2015-09-10 paper.tex
adding some refs

@@
 
-There is a planned shutdown of the Swiss Spallation Neutron Source (SINQ) in 2017, which provides an opportunity for changes to be made to the liquid deuterium cold neutron source.
-The 20 liter volume of liquid D$_2$ at approximately 25 K is located within the D$_2$O moderator tank surrounding the Pb spallation target.
+There is a planned shutdown of the Swiss Spallation Neutron Source (SINQ) in 2017, which provides an opportunity for changes to be made to the liquid deuterium cold neutron source \cite{upgrade}.
+The 20 liter volume of liquid D$_2$ at approximately 25 K is located within the D$_2$O moderator tank surrounding the lead spallation target.
 The innermost face of the cold source is approximately 35 cm away from the center of the target.
@@
 
-Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.6, with gains increasing with wavelength.
+Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.6, with gains increasing with wavelength \cite{atch_icans}.
 These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided.
@@
 Whenever a neutron undergoes a scattering reaction, the probability of scattering into the sphere's direction is calculated, a line is traced from the scattering location to the sphere's surface, and a neutron is generated there with a weight reduced by the scattering probability and the optical thickness of the medium in between.
-The generated neutrons are then transported normally inside the sphere \cite{mcnp}.
+The generated neutrons are then transported normally inside the sphere \cite{mcnp5}.
 This method served to preferentially scatter neutrons into the direction of the neutron guide.

### 2015-09-10 paper.tex
first draft done

@@
 Voiding the re-entrant hole relies on radiative heating to boil D$_2$ which in turn fills the re-entrant hole cavity, pushing the liquid D$_2$ out.
-Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D$_2$), removing some extra structural material around the D2 tank, redesigning the re-entrant hole geometry to be more optically ideal, introducing a Pb-208 reflector to minimize cold neutron up-scattering from the surrounding D$_2$O moderator tank, and implementing a small liquid H$_2$ volume to provide a cold neutron “hot spot” for certain instruments.
+Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D$_2$), redesigning the re-entrant hole geometry to be more optically ideal, introducing a Pb-208 reflector to minimize cold neutron up-scattering from the surrounding D$_2$O moderator tank, and implementing a small liquid H$_2$ volume to provide a cold neutron “hot spot” for certain instruments.
 These changes are predicted to increase neutron fluence between 1.1 to 2.0 times the current levels, depending on instrument location, view, and wavelengths of interest.
@@
 
-There is a planned shutdown of the Swiss Spallation Neutron Source (SINQ) in 2017, which provides an opportunity for changes to be made to the liquid deuterium cold neutron source \cite{upgrade}.
+There is a planned shutdown of the Swiss Spallation Neutron Source (SINQ) in 2017, which provides an opportunity for changes to be made to the liquid deuterium cold neutron source \cite{rueegg_icans}.
 The 20 liter volume of liquid D$_2$ at approximately 25 K is located within the D$_2$O moderator tank surrounding the lead spallation target.
@@
 
-Voiding the re-entrant hole relies on radiative heating to boil D$_2$ which in turn fills the re-entrant hole cavity, pushing the liquid D$_2$ out.
-Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D$_2$)
+The REH is presently a five-sided box with the open face at the bottom.
+It sits inside the D$_2$ volume directly next to the wall facing the guide hall.
+Voiding this kind of re-entrant hole relies on radiative heating to boil D$_2$ which in turn fills the re-entrant hole cavity with vapor, pushing the liquid D$_2$ out.
+Proposed plans include making the re-entrant hole external, ensuring that it is not filled with liquid D$_2$.
 
-Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.6, with gains increasing with wavelength \cite{atch_icans}.
-These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided.
+Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.9, with gains increasing with wavelength \cite{atch_icans}.
+These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided \cite{voided}.
 All future designs will have an external REH, which will decouple the fill level from radiation heating and ensure that the REH is never filled with liquid D$_2$.
@@
 Figure \ref{geom} shows a zoomed-in view of the important parts of the MCNP model geometry.
-A CAD model of the neutron guide bundles was converted to MCNP geometry by the MCAM software from XXX university in XXX China and integrated into the model \cite{mcam}.
-The target is made of Pb rods with zircalloy cladding and is cooled by D$_2$O, the moderator tank is filled with D$_2$O, the cold source is liquid D$_2$, the nozzles with a low-pressure helium mixture, and the shielding and neutron guide structure is steel.
+A CAD model of the neutron guide bundles was converted to MCNP geometry by the MCAM and integrated into the model \cite{mcam}.
+The target is made of lead rods with zircaloy cladding and is cooled by D$_2$O, the moderator tank is filled with D$_2$O, the cold source is liquid D$_2$, the nozzles with a low-pressure helium mixture, and the shielding and neutron guide structure is steel.
 All structural material in the moderator tank is AlMg3, which is shown in yellow in Figure \ref{geom}.
@@
 
-Two variance reduction methods were used in conjunction in order to perform the calculations in a reasonable amount of time.
-First, mesh-based weight windows were generated based on the response of a point detector located 75 cm from the neutron guide entrance.
-These windows serve to increase the number of neutrons that scatter inside the cold source while preserving the mean particle weight of an analog simulation by causing the neutrons in the moderator tank to carry a higher weight then be split into many lower-weight particles when they enter the cold source volume.
+Two variance reduction methods were used in conjunction to perform the simulations in a reasonable amount of time.
+First, mesh-based weight windows were generated based on the response of a point detector located inside the AMOR neutron guide, 75 cm from the entrance.
+The position gives the detector approximately a two degree view towards to cold source.
+The generated weight windows serve to increase the number of neutrons in regions that make large contributions to the point detector, which in this case is the cold source.
+In order to not bias simulation, the weight windwos cause neutrons entering the cold source are split into many neutrons with a lower statistical weight.
 
@@
 This tool is a non-physical sphere that is placed around the guide entrance that causes neutrons to be generated on its surface.
-Whenever a neutron undergoes a scattering reaction, the probability of scattering into the sphere's direction is calculated, a line is traced from the scattering location to the sphere's surface, and a neutron is generated there with a weight reduced by the scattering probability and the optical thickness of the medium in between.
-The generated neutrons are then transported normally inside the sphere \cite{mcnp5}.
-This method served to preferentially scatter neutrons into the direction of the neutron guide.
+Whenever a neutron undergoes a scattering reaction, the probability of scattering into the sphere's direction is calculated, a line is traced from the scattering location to the sphere's surface, and a neutron is generated at the surface with a weight reduced by the scattering probability and attenuation of the medium in-between.
+The generated neutrons are then transported normally inside the sphere \cite{mcnp5,mcnp6}.
+This method serves to preferentially scatter neutrons into the direction of the neutron guide instead of relying on probability to scatter them there.
 
@@
 A patch was developed at ORNL and PSI that implements the McStas guide reflectivity model in MCNPX 2.5.0 and 2.7.0 \cite{mcnp_reflectivity, EK_reflectivity}, but the model is analog and is not fully compatible with DXTRAN spheres.
-The implementation is analog in the sense that if a neutron is sampled to \emph{not} reflect on a guide surface, it is transmitted into the next cell.
+If a neutron is sampled to \emph{not} reflect on a guide surface, it is transmitted into the next cell.
 This means that neutron paths have to be sampled multiple times to account for any reflectivity losses, which slows the simulation down.
 
-Also, some stability issues were encountered while using the reflectivity patch in conjunction with the DXTRAN sphere.
-In order to ensure stable runs, a simulation was done first where a surface source was written at the guide entrance surface where any neutrons entering the guide were recorded and terminated.
-This source was used in a second simulation with the guide reflectivity turned on and used to transport the entering neutrons to the end of the guide where a tally was scored.
-Again, this process slowed the simulation down and made studies with many cases more difficult.
-An approximation to the guide response was used to eliminate the need for a second run to simply get the neutrons to the end of the guide.
+Some stability issues were also encountered while using the reflectivity patch in the same simulation as a DXTRAN sphere.
+In order to ensure stable runs, the simulation was split into two parts.
+First, a simulation was done where a surface source was written at the guide entrance surface.
+Any neutrons entering the guide were recorded and terminated.
+This source was then used in a second simulation with the guide reflectivity activiated.
+This step transported the entering neutrons to the end of the guide where a tally was scored.
+Again, this process slowed the simulation down since two MCNP simulations needed to be made for each case.
+A guide response approximation was used to eliminate the second run, which simply served to transport the neutrons to the end of the guide.
 
@@
 
-The guide reflectivity model implemented in MCNP is identical to that used in McStas.
+The guide reflectivity model implemented in MCNP is identical to that used in McStas \cite{mcnp_reflectivity}.
 The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq.
-\ref{eq:ref}.
+\ref{eq:ref} \cite{mcstas}.
 The values shown are the same for all the guides in the SINQ hall \cite{SINQ_guide_values}.
@@
 
-Since the neutron reflection probability is based on momentum transfer and the reflections are specular, it is determined by the incident neutron angle and energy.
-If the guide is rectangular, the reflection probability will not change as the neutron travels down the guide since the reflection angle will remain constant.
+Since the neutron reflection probability is based on momentum transfer and the reflections are specular, the probability is determined by the incident neutron angle and energy.
+If the guide is rectangular, the reflection probability will not change as the neutron travels down the guide since the reflection angle remains constant.
 These conditions mean that the exiting neutron current should be completely defined by the incident polar angle and energy of a neutron entering the guide.
@@
 In order to approximate the neutron current exiting the guide, a number of fixed-source runs of MCNPX were done as precalculations to the parametric study.
-An evenly-distributed source was defined at the entrance surface of the guide that emits neutrons in a polar angle bin $1/8^\circ$ wide and logarithmically in energy (to ensure low energies are sampled fairly).
+An evenly-distributed source was defined at the entrance surface of the guide that emits neutrons in a polar angle bin $1/8^\circ$ wide and logarithmically in energy (to ensure low energies are sampled well).
 The exiting current at the end of the guide was tallied and divided by the entrance current to yield a transfer function in energy for the polar angle of the source.
-This was done for $0-7.5^\circ$ of polar angle to yield the set of 60 functions shown in figure \ref{xfer_func}.
-The colors mean????
+This was done for 0 to 7.5 degrees of polar angle to yield the set of 60 functions shown in figure \ref{xfer_func}.
+Blue curves are those for incident angles that have an integer value of 0 degrees (e.g.
+0.125, 0.250, etc.), green curves for 1, red curves for 2, and so on.
+The set clearly shows that incident angles above 2 degrees make no contributions to wavelengths shorter than 8 \AA{} in the exit spectrum, and incident angles above 4 degrees make no contributions to wavelengths shorter than 16 \AA{}.
 
@@
 \begin{center}
-\includegraphics[scale=0.3,trim={2cm 1.7cm 2cm 0.8cm},clip]{graphics/xfer_func.pdf}
+\includegraphics[scale=0.3,trim={2cm 1.7cm 1.8cm 0.8cm},clip]{graphics/xfer_func.pdf}
 \end{center}
@@
 
-In order to verify that the reconstruction method works as expected, a comparison to the spectrum calculated by the explicit model was made.
-As mentioned previously, a surface source was written at the guide entrance, then this was used as the source for a second run with the guide reflectivity activated.
-During this run, the entry and exit current was tallied.
-The entry current was binning in polar angle according to the divisions in the pre-calculated transfer functions.
-The results of the comparison are shown in Figure \ref{xfer_bench}.
-The green line is the integrated neutron spectrum at the guide entrance, the blue line is the integrated exit current that was tallied at the guide exit, and the red curve is the exit spectrum calculated by multiplying the entrance spectrum by the transfer functions (and then summing them).
-The maximum error seen is about XXX\%, and decreases with energy, and has a 1-norm value of XXX\%.
+In order to verify that the reconstruction method works as expected, a comparison was made to an exit spectrum calculated with reflectivity model activated.
+As mentioned previously, a surface source was first written at the guide entrance, then this was used as the source for a second run with the guide reflectivity model activated.
+During the second run, the entry and exit current was tallied.
+The entry current was binned in polar angle according to the divisions in the pre-calculated transfer functions.
+The exit spectrum was the approximated by   The results of the comparison are shown in Figure \ref{xfer_bench}.
+The green line is the total, integrated neutron spectrum at the guide entrance, the blue line is the integrated exit current that was trnaported by the reflectivity model and tallied at the guide exit (the benchmark), and the red curve is the reconstructed exit spectrum.
+The maximum error seen is about 70\% at 0.55 \AA{}, but decreases with energy and is almost always within the statistical error of the simulation.
+The average 1-norm value (norm divided by number of bins) of the relative error is 7.8\%, and the average 2-norm value is 0.8\%.
 
@@
 \begin{center}
-\includegraphics[scale=0.4]{graphics/xfer_bench.pdf}
+\includegraphics[scale=0.5]{graphics/xfer_bench.pdf}
 \end{center}
-\caption{\label{xfer_bench}The reconstructed guide exit current compared to the exit current calculated with a MCNP simulation with guide reflectivity activated.}
+\caption{\label{xfer_bench}The reconstructed guide exit current compared to the exit current calculated with a MCNP simulation with guide reflectivity activated.
+The right axis is for the exit spectra and the left axis is for the entrance spectrum.
+The lower plot shows the recontruction relative error compared to the reflectivity simulation.
+The green envelope is the 1-sigma relative error of the reflectivity simulation.}
 \end{figure}
@@
 
-The re-entrant hole parametric study was done to investigate a wide range of geometries in the horizontal plane, where the guide width is smaller than the hole size.
-Four REH depths (14, 10, 6, 2 cm), four opening widths (4, 8, 12, 16 cm), and eleven hole slopes (-0.5, -0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5) were investigated in the study for a total of 176 cases.
+The re-entrant hole parametric study was done to investigate a wide range of geometries in the horizontal plane, where the guide width is smaller than the hole size and all the guides have different view angles.
+Four REH depths (14, 10, 6, 2 cm), four opening widths (4, 8, 12, 16 cm), and eleven hole slopes (-0.5, -0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5) were investigated in the study, totalling 176 cases.
 Figure \ref{parametric_geom} shows the parameters in relation to the cold source geometry.
-The REH vertical dimensions were chosen to be the full width of the nozzle with a slight tapering slope inward.
+The REH vertical dimensions were chosen to be the full width of the nozzle with a slightly tapering inward slope.
 The vertical dimensions were kept constant in this study, but will be the focus of future work.
@@
 With all of the variance reduction and approximations implemented, each case took about one hour to run on a 144-core configuration on a computer cluster at PSI.
-The spectra from all the cases are shown in upper plot in Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
-The figure of merit was chosen to be the total current exiting the guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall.
+The spectra from all the cases are shown in upper plot of Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
+The figure of merit was chosen to be the total current exiting the guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.
 The parameters were varied in slope-width-depth order, with slope being the fasted varied parameter.
 Figure \ref{parametric_REH} has labeled, colored blocks in the lower plot to show which parameters are constant for that block.
-Slope and opening width have the most affect on performance at large depths.
+Slope and opening width have the most affect on exit current at large hole depths.
 
@@
 \end{center}
-\caption{\label{parametric_gain}The gain factor of the neutron guide exit current of best-performing REH geometry over the REH being absent.}
+\caption{\label{parametric_gain}The gain factor of the neutron guide exit current of best-performing REH geometry over the REH being absent.  The thick red line is the data smoothed over 15 bins.}
 \end{figure}
@@
 
-From this study and the requirements it imposed on the simulation method, it can be concluded that the flux reconstruction method has been verified to be at least self-consistent, and that a near-optimal horizontal REH geometry has been determined.
-The REH increases total exit current by 1.24\% on average from 3-6 \AA{} with a peak gain of 1.29 at 5.5 \AA{}.
+From this study, it can be concluded that the flux reconstruction method is at least self-consistent, and that a near-optimal horizontal REH geometry has been determined.
+The REH increases total exit current by a factor of 1.24 on average from 3-6 \AA{} with a peak gain of 1.29 at 5.5 \AA{}.
 
@@
 Different types of reflector materials and configurations will also be investigated.
-The refector sits behind the cold source on the side opposite the target and reducing cold neutron losses in it may increase the guide exit current.
+The refector sits behind the cold source (the side opposite the target), and reducing cold neutron losses in it may increase the guide exit current.
 Adding a belt of liquid H$_2$ to produce a ``cold spot'' for focusing instruments will also be investigated.
@@
 
-Further development of the guide reflectivity patch for MCNP 6.1 will also be done.
-Specifically, making a switch to reduce neutron weight upon reflection instead of leaking non-reflected neutrons in order to speed up in-beam calculations where this signal is of interest and not the noise.
+A guide reflectivity patch will be made for MCNP 6.1 will also be done.
+Ideally, it will also include a switch to reduce neutron weight upon reflection instead of leaking non-reflected neutrons.
+This should help speed up in-beam calculations where this signal is of interest and not the noise.
 

### 2015-09-15 paper.tex
first draft done
typos

@@
 The generated weight windows serve to increase the number of neutrons in regions that make large contributions to the point detector, which in this case is the cold source.
-In order to not bias simulation, the weight windwos cause neutrons entering the cold source are split into many neutrons with a lower statistical weight.
+In order to not bias simulation, the weight windows cause neutrons entering the cold source are split into many neutrons with a lower statistical weight.
 
@@
 
-In conjunction with the variance reduction methods described in the previous section, an approximation to how the neutron geuides transport neutrons was also used.
+In conjunction with the variance reduction methods described in the previous section, an approximation to how the neutron guides transport neutrons was also used.
 A patch was developed at ORNL and PSI that implements the McStas guide reflectivity model in MCNPX 2.5.0 and 2.7.0 \cite{mcnp_reflectivity, EK_reflectivity}, but the model is analog and is not fully compatible with DXTRAN spheres.
@@
 Any neutrons entering the guide were recorded and terminated.
-This source was then used in a second simulation with the guide reflectivity activiated.
+This source was then used in a second simulation with the guide reflectivity activated.
 This step transported the entering neutrons to the end of the guide where a tally was scored.
@@
 The exit spectrum was the approximated by   The results of the comparison are shown in Figure \ref{xfer_bench}.
-The green line is the total, integrated neutron spectrum at the guide entrance, the blue line is the integrated exit current that was trnaported by the reflectivity model and tallied at the guide exit (the benchmark), and the red curve is the reconstructed exit spectrum.
+The green line is the total, integrated neutron spectrum at the guide entrance, the blue line is the integrated exit current that was transported by the reflectivity model and tallied at the guide exit (the benchmark), and the red curve is the reconstructed exit spectrum.
 The maximum error seen is about 70\% at 0.55 \AA{}, but decreases with energy and is almost always within the statistical error of the simulation.
@@
 The right axis is for the exit spectra and the left axis is for the entrance spectrum.
-The lower plot shows the recontruction relative error compared to the reflectivity simulation.
+The lower plot shows the reconstruction relative error compared to the reflectivity simulation.
 The green envelope is the 1-sigma relative error of the reflectivity simulation.}
@@
 \caption{\label{parametric_geom}The geometry varied in the REH parametric study. ``A'' is the hole depth, ``B'' is the opening width, and ``C'' is the hole slope.}
-\end{minipage}\hspace{5pc}%
+\end{minipage}\hfill%
 \begin{minipage}{11pc}
@@
 Different types of reflector materials and configurations will also be investigated.
-The refector sits behind the cold source (the side opposite the target), and reducing cold neutron losses in it may increase the guide exit current.
+The reflector sits behind the cold source (the side opposite the target), and reducing cold neutron losses in it may increase the guide exit current.
 Adding a belt of liquid H$_2$ to produce a ``cold spot'' for focusing instruments will also be investigated.

### 2015-09-16 paper.tex
revisions

@@
 
-\begin{abstract}Changing the configuration of the cold neutron source during an extended shutdown of Swiss Spallation Neutron Source (SINQ) is being considered for improving performance of the instruments that use the cold source.
+\begin{abstract}Changing the configuration of the cold neutron source during an extended shutdown of the Swiss Spallation Neutron Source (SINQ) is being considered for improving performance of the instruments that use the cold source.
 The cold neutron source consists of a 20 L volume of liquid D$_2$ at approximately 25 K.
 Previous upgrades included adding a re-entrant hole into one side of the D$_2$ volume to allow cold neutrons to stream uninhibited from the center of the source towards the instrument neutron guides.
-Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.6, with gains increasing with wavelength.
-These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided.
+Calculations done prior to these changes predicted cold neutron fluence gains from 1.2 to 1.9, with gains increasing with wavelength.
+These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided in the present design.
 Voiding the re-entrant hole relies on radiative heating to boil D$_2$ which in turn fills the re-entrant hole cavity, pushing the liquid D$_2$ out.
-Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D$_2$), redesigning the re-entrant hole geometry to be more optically ideal, introducing a Pb-208 reflector to minimize cold neutron up-scattering from the surrounding D$_2$O moderator tank, and implementing a small liquid H$_2$ volume to provide a cold neutron “hot spot” for certain instruments.
-These changes are predicted to increase neutron fluence between 1.1 to 2.0 times the current levels, depending on instrument location, view, and wavelengths of interest.
+Proposed plans include making the re-entrant hole external (ensuring that it is not filled with liquid D$_2$) and redesigning the re-entrant hole geometry to be more optically ideal.
 \end{abstract}
@@
 In the planned upgrade strategies, no changes to the surrounding aluminum and zirconium safety hulls will be made, and no changes to the insert tube structure will be made.
-I.e., all changes must fit into the existing multi-walled insert geometry.
+In other words, all changes must fit into the existing multi-walled insert geometry.
 
@@
 
-The goal of the re-entrant hole (REH) is to remove scattering and absorbing material between the cold neutron maximum and the direction of interest.
-In this case, the cold neutron maximum is at the center of the cold source and the direction of interest is towards the SINQ guide hall.
+The goal of the re-entrant hole (REH) is to remove scattering and absorbing material between the spot with the maximum cold neutron flux and the direction of interest.
+In this case, this spot is at the center of the cold source and the direction of interest is towards the SINQ guide hall.
 
@@
 These increases have not been observed, and it is suspected that the re-entrant hole is not fully voided \cite{voided}.
-All future designs will have an external REH, which will decouple the fill level from radiation heating and ensure that the REH is never filled with liquid D$_2$.
+All future designs will have an external REH, which will decouple the fill level from radiation heating and ensure that the REH is never filled with D$_2$.
 
@@
 A CAD model of the neutron guide bundles was converted to MCNP geometry by the MCAM and integrated into the model \cite{mcam}.
-The target is made of lead rods with zircaloy cladding and is cooled by D$_2$O, the moderator tank is filled with D$_2$O, the cold source is liquid D$_2$, the nozzles with a low-pressure helium mixture, and the shielding and neutron guide structure is steel.
+The target is made of lead rods with zircaloy cladding and is cooled by D$_2$O, the moderator tank is filled with D$_2$O, the cold source is liquid D$_2$, the nozzles are filled with a low-pressure helium mixture, and the shielding and neutron guide structure is steel.
 All structural material in the moderator tank is AlMg3, which is shown in yellow in Figure \ref{geom}.
@@
 \begin{center}
-\includegraphics[trim={9.2cm 8cm 4cm 8cm},clip]{graphics/geom.pdf}
+\includegraphics[trim={9.2cm 8cm 4cm 8cm},clip]{graphics/geom2.pdf}
 \end{center}
@@
 Two variance reduction methods were used in conjunction to perform the simulations in a reasonable amount of time.
-First, mesh-based weight windows were generated based on the response of a point detector located inside the AMOR neutron guide, 75 cm from the entrance.
-The position gives the detector approximately a two degree view towards to cold source.
+First, mesh-based weight windows were generated based on the response of a point detector located inside the AMOR neutron guide.
+The point detector was positioned 75 cm from the guide entrance, giving it an approximately a two degree view towards the cold source.
 The generated weight windows serve to increase the number of neutrons in regions that make large contributions to the point detector, which in this case is the cold source.
-In order to not bias simulation, the weight windows cause neutrons entering the cold source are split into many neutrons with a lower statistical weight.
+In order to not bias the simulation, the weight windows cause neutrons entering the cold source to be split into many neutrons with a lower individual statistical weight.
 
-The second variance reduction method used is a ``DXTRAN'' sphere.
+The second variance reduction method used was a ``DXTRAN'' sphere.
 This tool is a non-physical sphere that is placed around the guide entrance that causes neutrons to be generated on its surface.
-Whenever a neutron undergoes a scattering reaction, the probability of scattering into the sphere's direction is calculated, a line is traced from the scattering location to the sphere's surface, and a neutron is generated at the surface with a weight reduced by the scattering probability and attenuation of the medium in-between.
+Whenever a neutron undergoes a scattering reaction, the probability of scattering into the sphere's direction is calculated, a line is traced from the scattering location to the sphere's surface, and a new neutron is generated at the surface with a weight reduced by the scattering probability and material attenuation.
 The generated neutrons are then transported normally inside the sphere \cite{mcnp5,mcnp6}.
-This method serves to preferentially scatter neutrons into the direction of the neutron guide instead of relying on probability to scatter them there.
+This method serves to preferentially scatter neutrons into the direction of the neutron guide instead of relying on probability to transport them there.
 
@@
 
-In conjunction with the variance reduction methods described in the previous section, an approximation to how the neutron guides transport neutrons was also used.
+In conjunction with the variance reduction methods described in the previous section, an approximation to the neutron guides was also used.
 A patch was developed at ORNL and PSI that implements the McStas guide reflectivity model in MCNPX 2.5.0 and 2.7.0 \cite{mcnp_reflectivity, EK_reflectivity}, but the model is analog and is not fully compatible with DXTRAN spheres.

### 2015-09-16 paper.tex
revisions

@@
 All structural material in the moderator tank is AlMg3, which is shown in yellow in Figure \ref{geom}.
+The cross sections used in the simulations were from the ENDF/B-VII.1 library.
+Thermal scattering S($\alpha$,$\beta$) tables (continuous-energy when possible) were used for both moderators and structural materials within the moderator tank \cite{sab}.
 
@@
 First, a simulation was done where a surface source was written at the guide entrance surface.
+In this first simulation, the DXTRAN sphere surrounds the guide entrance.
 Any neutrons entering the guide were recorded and terminated.
-This source was then used in a second simulation with the guide reflectivity activated.
+This source was then used in a second simulation with the guide reflectivity activated and without the DXTRAN sphere.
 This step transported the entering neutrons to the end of the guide where a tally was scored.
 Again, this process slowed the simulation down since two MCNP simulations needed to be made for each case.
-A guide response approximation was used to eliminate the second run, which simply served to transport the neutrons to the end of the guide.
+Thus, a guide response approximation was used to eliminate the need for a second run, which simply served to transport the neutrons to the end of the guide.
 
@@
 The guide reflectivity model implemented in MCNP is identical to that used in McStas \cite{mcnp_reflectivity}.
-The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq.
+The reflectivity curve for the current AMOR guide is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq.
 \ref{eq:ref} \cite{mcstas}.
-The values shown are the same for all the guides in the SINQ hall \cite{SINQ_guide_values}.
+The values shown are the same for all the straight guides in the SINQ hall \cite{SINQ_guide_values}.
+The dimensions of the guides are slightly different, however, as can be seen from their horizontal cross sections in Figure \ref{geom}.
 
@@
 These conditions mean that the exiting neutron current should be completely defined by the incident polar angle and energy of a neutron entering the guide.
-The position in the guide entrance will determine the phase of the exiting rays, but if the entire exit surface is summed over, this phase becomes irrelevant.
+The vertical and horizontal position in the guide entrance determines the where neutrons exit the guide, but if the exit current is integrated over exit postition, exit position becomes irrelevant and only the transmission probability matters.
 
@@
 
-In order to approximate the neutron current exiting the guide, a number of fixed-source runs of MCNPX were done as precalculations to the parametric study.
+In order to approximate the spatially-integrated neutron spectrum at the guide exit, a number of fixed-source runs of MCNPX were done as precalculations to the parametric study.
 An evenly-distributed source was defined at the entrance surface of the guide that emits neutrons in a polar angle bin $1/8^\circ$ wide and logarithmically in energy (to ensure low energies are sampled well).
@@
 \end{center}
-\caption{\label{xfer_func}Set of transfer functions for a m=2 guide.}
+\caption{\label{xfer_func}Set of transfer functions for a $m=2$ guide.}
 \end{figure}
@@
 
-In order to verify that the reconstruction method works as expected, a comparison was made to an exit spectrum calculated with reflectivity model activated.
-As mentioned previously, a surface source was first written at the guide entrance, then this was used as the source for a second run with the guide reflectivity model activated.
+In order to verify that the reconstruction method works as expected, a comparison was made to an exit spectrum calculated without using the approximation.
+To calulated the exit spectrum, a surface source was first written at the guide entrance using a DXTRAN sphere.
+This surface source was then used in a second run with the guide reflectivity model activated.
 During the second run, the entry and exit current was tallied.
-The entry current was binned in polar angle according to the divisions in the pre-calculated transfer functions.
-The exit spectrum was the approximated by   The results of the comparison are shown in Figure \ref{xfer_bench}.
+The entry current was binned in polar angle according to the divisions in the pre-calculated transfer functions and was used to reconstruct the exit spectrum so it could be compared to the exit tally.
+The results of the comparison are shown in Figure \ref{xfer_bench}.
 The green line is the total, integrated neutron spectrum at the guide entrance, the blue line is the integrated exit current that was transported by the reflectivity model and tallied at the guide exit (the benchmark), and the red curve is the reconstructed exit spectrum.
@@
 
-The re-entrant hole parametric study was done to investigate a wide range of geometries in the horizontal plane, where the guide width is smaller than the hole size and all the guides have different view angles.
+The re-entrant hole parametric study was done to investigate a wide range of geometries differing in the horizontal plane, where the guide width is smaller than the hole size and all the guides have different view angles.
 Four REH depths (14, 10, 6, 2 cm), four opening widths (4, 8, 12, 16 cm), and eleven hole slopes (-0.5, -0.4, -0.3, -0.2, -0.1, 0.0, 0.1, 0.2, 0.3, 0.4, 0.5) were investigated in the study, totalling 176 cases.
@@
 \end{center}
-\caption{\label{parametric_geom}The geometry varied in the REH parametric study. ``A'' is the hole depth, ``B'' is the opening width, and ``C'' is the hole slope.}
+\caption{\label{parametric_geom}The geometric dimensions varied in the REH parametric study. ``A'' is the hole depth, ``B'' is the opening width, and ``C'' is the hole slope.}
 \end{minipage}\hfill%
@@
 \end{center}
-\caption{\label{case077}The best-performing horizontal geometry for the REH.}
+\caption{\label{case077}Horizontal cut of the cold source D$_2$ volume showing the best-performing geometry for the REH.}
 \end{minipage} 
@@
 With all of the variance reduction and approximations implemented, each case took about one hour to run on a 144-core configuration on a computer cluster at PSI.
-The spectra from all the cases are shown in upper plot of Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
-The figure of merit was chosen to be the total current exiting the guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.
-The parameters were varied in slope-width-depth order, with slope being the fasted varied parameter.
+The spectra from all the cases are shown in the upper plot of Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
+The figure of merit was chosen to be the total current exiting the AMOR guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.
+The parameters were varied in slope-width-depth order, with slope being the fastest varied parameter.
 Figure \ref{parametric_REH} has labeled, colored blocks in the lower plot to show which parameters are constant for that block.
-Slope and opening width have the most affect on exit current at large hole depths.
+Slope and opening width have the most effect on the exit current at large hole depths.
 
@@
 \end{center}
-\caption{\label{parametric_gain}The gain factor of the neutron guide exit current of best-performing REH geometry over the REH being absent.  The thick red line is the data smoothed over 15 bins.}
+\caption{\label{parametric_gain}The gain factor of the neutron guide exit current of best-performing REH geometry over the REH being absent.
+The thick, red line is the simulation data smoothed over 15 bins.}
 \end{figure}
@@
 Figure \ref{parametric_gain} shows the gain from the best performing REH geometry over an absent REH.
-The maximum gain 1.29 at 5.5 \AA{} and its average value from 3-6 \AA{} is 1.24.
+The maximum gain is 1.29 at 5.5 \AA{} and its average value from 3-6 \AA{} is 1.24.
 Similar gains should be seen by all instruments in the SINQ guide hall.
-The drop in gain after 5.5 \AA{} is suspected to be from the liquid D$_2$ cross section dropping from about 5.5 to 25 \AA{}, making it more transparent to colder neutrons and reducing the re-entrant hole's benefits.
+The drop in gain after 5.5 \AA{} is suspected to be from the liquid D$_2$ cross section decreasing between 5.5 to 25 \AA{}, making it more transparent to colder neutrons and reducing the re-entrant hole's benefits.
 
@@
 
-From this study, it can be concluded that the flux reconstruction method is at least self-consistent, and that a near-optimal horizontal REH geometry has been determined.
-The REH increases total exit current by a factor of 1.24 on average from 3-6 \AA{} with a peak gain of 1.29 at 5.5 \AA{}.
+From this study, it can be concluded that the flux reconstruction method is at least self-consistent, and can speed up calculations significantly.
+Furthermore, a near-optimal horizontal REH geometry has been determined.
+The REH increases total exit current for wavelengths of 3-6 \AA{} by a factor of 1.24 on average.
+The peak gain is 1.29 at a wavelength of 5.5 \AA{}.
 
@@
 
-This study has only determined the horizontal geometry of the re-entrant hole in the cold source at SINQ.
-Another study is needed to investigate REH sensitivity to vertical changes, as well as a parametric study over a smaller range near the optimal point to determine more exact dimensions.
-The affect the REH has on the neutron flux on the opposite side will also be determined.
+This study has only determined the optimal horizontal geometic dimensions of the re-entrant hole in the cold source at SINQ.
+Another study is needed to investigate REH sensitivity to changes in the vertical dimensions, as well as a parametric study over a smaller range near the optimal point to determine more exact dimensions.
+The effect the REH has on the neutron flux on the opposite side of the cold source will also be determined.
 
@@
 
-A guide reflectivity patch will be made for MCNP 6.1 will also be done.
+A guide reflectivity patch for MCNP 6.1 will also be done.
 Ideally, it will also include a switch to reduce neutron weight upon reflection instead of leaking non-reflected neutrons.

### 2015-09-16 paper.tex
last revisions for now

@@
 
-The geometry of the best-performing case is shown in figure \ref{case077}.
-The depth is 10 cm, the opening width is 12 cm, and the slope is 0.5.
-This opening is as wide as the nozzle and almost tapers to a point at the maximum depth.
-The maximum depth is 4 cm from the radial center of the cold source.
-
 \begin{figure}
 \begin{center}
-\includegraphics[scale=0.38,trim={1cm 2.35cm 1cm 0cm},clip]{graphics/parametric_REH.pdf}
+\includegraphics[scale=0.26,trim={0cm 0cm 0cm 0cm},clip]{graphics/parametric_REH.pdf}
 \end{center}
-\caption{\label{parametric_REH}The envelope formed by the spectra from all 176 cases considered (upper) and their figures of merit (lower) which is total current from 3 to 6 \AA{}.}
+\caption{\label{parametric_REH}The envelope formed by the spectra from all 176 cases considered (upper) and their figures of merit (lower) which is total current from 3 to 6 \AA{}.
+Case000 is the case with the REH completely filled.}
 \end{figure}
@@
 \end{figure}
+
+The geometry of the best-performing case is shown in figure \ref{case077}.
+The depth is 10 cm, the opening width is 12 cm, and the slope is 0.5.
+This opening is as wide as the nozzle and almost tapers to a point at the maximum depth.
+The maximum depth is 4 cm from the radial center of the cold source.
 

### 2015-09-16 paper.tex
revisions

@@
 Two variance reduction methods were used in conjunction to perform the simulations in a reasonable amount of time.
-First, mesh-based weight windows were generated based on the response of a point detector located inside the AMOR neutron guide.
+First, mesh-based weight windows were generated based on the response of a point detector located inside the AMOR/SANS-I neutron guide.
 The point detector was positioned 75 cm from the guide entrance, giving it an approximately a two degree view towards the cold source.
@@
 The guide reflectivity model implemented in MCNP is identical to that used in McStas \cite{mcnp_reflectivity}.
-The reflectivity curve for the current AMOR guide is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq.
+The reflectivity curve for the current AMOR/SANS-I guide is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq.
 \ref{eq:ref} \cite{mcstas}.
@@
 The spectra from all the cases are shown in the upper plot of Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
-The figure of merit was chosen to be the total current exiting the AMOR guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.
+The figure of merit was chosen to be the total current exiting the AMOR/SANS-I guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.
 The parameters were varied in slope-width-depth order, with slope being the fastest varied parameter.

### 2015-10-02 paper.tex
changes, polish

@@
 
-There is a planned shutdown of the Swiss Spallation Neutron Source (SINQ) in 2017, which provides an opportunity for changes to be made to the liquid deuterium cold neutron source \cite{rueegg_icans}.
-The 20 liter volume of liquid D$_2$ at approximately 25 K is located within the D$_2$O moderator tank surrounding the lead spallation target.
-The innermost face of the cold source is approximately 35 cm away from the center of the target.
+The Swiss Spallation Neutron Source (SINQ) is a spallation neutron source driven by a continuous 590 MeV proton beam at the Paul Scherrer Institut in Villigen, Switzerland.
+The incoming protons impinge on a lead target cooled with heavy water, producing high energy neutrons.
+These neutrons are moderated by the tank of D$_2$O surrounding the target.
+The cold source is a 20 liter volume of liquid D$_2$ at approximately 25 K located within the D$_2$O moderator tank with its innermost face approximately 35 cm away from the center of the target.
+It serves to further reduce the energies of the ``thermal'' neutrons coming from the D$_2$O tank into a regime that is more useful to instruments which receive neutrons from its surface.
+Neutrons are transported from the cold source to the intruments via neutron guides, which are internally coated with neutron ``supermirrors'', which are reflective to neutrons at low energies and low indcient angles \cite{mcnp_reflectivity}.
+
+There is an extended shutdown of SINQ ambitiously planned for 2018 which will provide an opportunity for changes to be made to the cold neutron source \cite{rueegg_icans}.
 In the planned upgrade strategies, no changes to the surrounding aluminum and zirconium safety hulls will be made, and no changes to the insert tube structure will be made.
 In other words, all changes must fit into the existing multi-walled insert geometry.
+This paper presents a parametric study on changes to the physical dimensions of cold source and the predicted effects these changes have on the integral neutron in the neutron guides.
 
@@
 
-The goal of the re-entrant hole (REH) is to remove scattering and absorbing material between the spot with the maximum cold neutron flux and the direction of interest.
+The goal of a re-entrant hole (REH) is to remove scattering and absorbing material between the spot with the maximum cold neutron flux and the direction of interest.
 In this case, this spot is at the center of the cold source and the direction of interest is towards the SINQ guide hall.
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 These conditions mean that the exiting neutron current should be completely defined by the incident polar angle and energy of a neutron entering the guide.
-The vertical and horizontal position in the guide entrance determines the where neutrons exit the guide, but if the exit current is integrated over exit postition, exit position becomes irrelevant and only the transmission probability matters.
+The vertical and horizontal position in the guide entrance determines where neutrons exit the guide, but if the exit current is integrated over exit position, exit position becomes irrelevant and only the transmission probability matters.
 
@@
 \begin{center}
-\includegraphics[scale=0.3,trim={2cm 1.7cm 1.8cm 0.8cm},clip]{graphics/xfer_func.pdf}
+\includegraphics[scale=0.3,trim={4cm 0.5cm 0cm 0cm},clip]{graphics/xfer_func.pdf}
 \end{center}
@@
 The spectra from all the cases are shown in the upper plot of Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.
-The figure of merit was chosen to be the total current exiting the AMOR/SANS-I guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.
+The figure of merit was chosen to be the total current exiting the AMOR/SANS-I guide six meters from the cold source surface from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.
 The parameters were varied in slope-width-depth order, with slope being the fastest varied parameter.
@@
 
-\section{Conculsions}
+\section{Conclusions}
 
@@
 
-This study has only determined the optimal horizontal geometic dimensions of the re-entrant hole in the cold source at SINQ.
-Another study is needed to investigate REH sensitivity to changes in the vertical dimensions, as well as a parametric study over a smaller range near the optimal point to determine more exact dimensions.
+The optimal horizontal dimensions of the REH have been determined, another study is needed to investigate REH sensitivity to changes in the vertical dimensions.
 The effect the REH has on the neutron flux on the opposite side of the cold source will also be determined.
-
 Different types of reflector materials and configurations will also be investigated.
